---
title: "ADA-PARC"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    theme: flatly
---

```{r setup, include=FALSE}

# ====================
# Setup
# ====================

# Packages
library(tidyverse); library(readxl); library(openxlsx); library(summarytools); library(janitor); 
library(sf); library(urbnmapr); library(leaflet); library(leaflet.extras);
library(htmltools); library(shiny); library(shinyWidgets); library(flexdashboard); 
library(colourpicker); library(DT); library(highcharter);
library(scales); library(hrbrthemes); library(ggthemes)

# Must install urbnmapr via GitHUb if is not already installed
# install.packages("devtools")
# devtools::install_github("UrbanInstitute/urbnmapr")

```



Home
============================================================================

Sidebar {.sidebar}
-----------------------------------------------------------------------

<br>

#### How to Navigate<br>this Website

<br>

Use the **National** tab to examine the status of people with disabilities at the national and state level.  

Use the **By Metro** tab to investigate transit accessibility to jobs and housing by county or city.

Use the **Download** tab to get the raw data powering this dashboard and as well as pre-formatted fact sheets a specific area of interest.

Use the **Accessibility** tab to set color palettes for the visualizations in this dashboard.  

<br>

Application author:

[Sean Connelly](https://sean-connelly.github.io/) and [Ethan Jantz](https://ethanjantz.github.io/)
[Voorhees Center](https://voorheescenter.uic.edu/)

Row
-----------------------------------------------------------------------

### 

<br>

Welcome to the ADA-PARC website. The ADA-PARC is a collaborative research project of 7 Americans with Disabilities Act (ADA) Regional Centers.

<br>

#### Purpose of ADA-PARC

The ADA-PARC research has four purposes:

  1. **To look at participation disparities** experienced by people with disabilities post ADA & Olmstead
  2. **To identify & examine key environmental factors** contributing to these disparities
  3. **To benchmark participation disparities and highlight promising practices** at state & city levels
  4. **To action-plan strategies for dissemination and utilization of findings** to be used by ADA Centers and others in community capacity building & systems change initiatives

<br>

#### The Work of the ADA-PARC

The ADA-PARC has research teams focused on Community Living, Community Participation & Work/Economic Participation measures and uses Regional Steering Committees in each of the seven participating regions to gather, review, and choose appropriate data to achieve the project's purposes. The data are mainly from national data sources that have enough statistical power to be relevant on the local level.

The intent of this effort is to use this information to inform:

  1. ADA Center technical assistance and resource dissemination, and
  2. Community level stakeholders to increase participation opportunities in their communities.

<br>

#### Who is the ADA-PARC

The seven participating ADA-Regional Centers in the ADA-PARC are:

  - Region 6 Southwest ADA Center: Lex Frieden, Co-Project Director
  - Region 5 Great Lakes ADA Center: Joy Hammel, Co-Project Director, Community Participation data team lead
  - Region 9 Pacific ADA Center: Lewis Kraus, Community Living data team lead
  - Region 4 Southeast ADA Center: Katie McDonald, Work & Economics data team lead
  - Region 8 Rocky Mountain ADA Center: Bob Gattis
  - Region 3 Mid-Atlantic ADA Center: Marian Vessels
  - Region 10 Great Northwest ADA Center: Kathe Matrone

<br>

#### About this Website

The ADA-PARC website is a collection of public data sets that can help shed light on the status of people with disabilities in local communities. The data includes national, state, county, and city data. In addition to Demographic data describing the population, the three main areas of data to illuminate the status of disability in an area are: Community Living, Community Participation and Work & Economics. Each of the three areas presents data in map form as well as in tabular form. A summary of what is important about the data is presented on each page. The data source is described along with the calculation to arrive at the values used in the tables and maps. Data is first presented by state, and then if available, at county and city level.
Accessibility

To learn about the accessibility features of this website, please see the Accessibility Statement at the bottom of any page.



Demographics {data-navmenu="National" data-icon="fa-user"}
======================================================================

```{r, national import}

# ====================
# Import data
# ====================

# Set database path
db_path <- "February 2020 update 2018 ACS/2.20.20DatabaseACS2018.final.xlsx"

# Demographics
demographics <- read_excel(path = db_path,
                           sheet = "Demographics", 
                           .name_repair = make_clean_names,
                           skip = 2) %>% 
  remove_empty(c("rows", "cols")) %>% 
  rename("abbrev" = state_abbreviation) %>% 
  mutate(across(-c(state:city), as.numeric))

# Community Living
community_living <- read_excel(path = db_path,
                               sheet = "Community Living",
                               .name_repair = make_clean_names,
                               skip = 2) %>% 
  remove_empty(c("rows", "cols")) %>% 
  mutate(across(-c(state:abbrev), as.numeric))

# Community Participation
community_participation <- read_excel(path = db_path,
                           sheet = "CommunityParticipation",
                           .name_repair = make_clean_names,
                           skip = 3) %>% 
  remove_empty(c("rows", "cols")) %>% 
  mutate(across(-c(state:city), as.numeric))

# Work and Economic
work_economic <- read_excel(path = db_path,
                           sheet = "WorkEconomic",
                           .name_repair = make_clean_names,
                           skip = 3) %>% 
  remove_empty(c("rows", "cols")) %>% 
  mutate(across(-c(state:city), as.numeric))

# Read in spatial data
states_sf <- get_urbn_map(map = "states", sf = TRUE)

```

Row {data-height=100}
-----------------------------------------------------------------------

### {.section-divider}

#### Overall

##### Percent of Total Population with Disabilities

Row {data-height=500}
-----------------------------------------------------------------------

### Map

```{r, demographics general map}

# Data for this section
demo_gen_data <- demographics %>% 
  filter(is.na(city)) %>% 
  select("state_name" = state, "state_abbv" = abbrev, 
         percent_of_total_population_with_a_disability, pwd, total_population) %>% 
  mutate(percent_of_total_population_with_a_disability =
           round(percent_of_total_population_with_a_disability, 1))

# SF data and palette
demo_gen_map_data <- demo_gen_data %>% 
    left_join(states_sf, ., by = c("state_name", "state_abbv")) %>% 
    st_transform(4326)

demo_gen_selected <- reactive({ "percent_of_total_population_with_a_disability" })

pal_demo1 <- reactive ({ 
  
  colorQuantile(palette = input$access_map_palette, 
                domain = pull(demo_gen_data, !!sym(demo_gen_selected())),
                n = 4)
  
})

# used in tandem with the template in setup, the title for the map
# as discussed, we can replace this with a built-in title function using leaflet
# title <- tags$div(
#   tag.map.title, HTML("Percent with Disabilities")
# )  
  
# State map
output$demo1map <- renderLeaflet({
  
  # Map
  demo1map <- demo_gen_map_data %>%
    mutate(map_focus = !!sym(demo_gen_selected())) %>% 
    leaflet() %>%
    clearShapes() %>%
    addResetMapButton() %>% 
    addPolygons(stroke = TRUE, color = "#444444", weight = 1, smoothFactor = 0, 
                fillColor = ~pal_demo1()(map_focus),
                fillOpacity = 1,
                popup = ~paste(state_name, " (", state_abbv, ")", "<br>",
                               percent(map_focus,
                                       scale = 1, accuracy = 0.1)),
                layerId = ~state_name) %>% 
    addLegend(position = "topright", pal = pal_demo1(),
              values = ~map_focus,
              labFormat =  function(type, cuts, p) {
                n = length(cuts)
                paste0(as.numeric(cuts)[-n], " &ndash; ", as.numeric(cuts)[-1])
              },
              title = paste0("PWD (%),<br>", input$demo_gen_type))
  
  demo1map
  
})

# Click event for the map
click_demo1map <- eventReactive(input$demo1map_shape_click, {
  
  x <- input$demo1map_shape_click
  y <- x$id
  
  return(y)

})

# Add the clicked state to the map, and remove when a new one is clicked
observe({
  
  req(click_demo1map())
  
  demo1map <- leafletProxy("demo1map") %>%
    removeShape("highlight_state") %>%
    addPolygons(data = demo_gen_map_data[demo_gen_map_data$state_name == click_demo1map(), ], 
                fill = FALSE, weight = 3,
                color = "#00FFFF", opacity = 1, layerId = "highlight_state")
  
})

# Fetch data for the clicked state
demo_gen_data_selected <- reactive({
  
  if(is.null(input$demo1map_shape_click)){
    demo_gen_data
  } else {
    demo_gen_data %>% 
      filter(state_name == click_demo1map())
  }
  
})

leafletOutput("demo1map")  

```

### Table {.wide-DT}

```{r, demographics general table}

# Data table
DT::renderDataTable({
  
  # Table
  DT::datatable(
    demo_gen_data_selected() %>% 
      rename("percent_pwd" = percent_of_total_population_with_a_disability,
             "total_pop" = total_population) %>% 
      mutate(percent_pwd = percent(percent_pwd, scale = 1, accuracy = 0.1),
             pwd = comma(pwd),
             total_pop = comma(total_pop)),
  options(scrollX = "200px"))
  
})

```

Row {data-height=100}
-----------------------------------------------------------------------

### {.section-divider}

#### Age

##### Percent of Persons 18-64, 65+ with Disability

Row {data-height=500}
-----------------------------------------------------------------------

### Map

```{r, demographics age map}

# Data for this section
demo_age_data <- demographics %>%
  filter(is.na(city)) %>%
  select("state_name" = state, "state_abbv" = abbrev,
         percent_people_18_64_with_a_disability, pwd_18_64_years, total_population18_64,
         percent_people_65_with_a_disability, pwd_65_years, total_population65) %>%
  mutate(across(starts_with("percent"), round, 1))

# SF data and palette
demo_age_map_data <- demo_age_data %>%
    left_join(states_sf, ., by = c("state_name", "state_abbv")) %>%
    st_transform(4326)

# Input for column to map
selectInput("demo_age_type",
            label = "Select a category",
            choices = c("18-64", "65+"),
            selected = "18-64")

demo_age_selected <- reactive({

  if (input$demo_age_type == "18-64"){
    "percent_people_18_64_with_a_disability"
  } else {
    "percent_people_65_with_a_disability"
  }

})

pal_demo2 <- reactive ({ 
  
  colorQuantile(palette = input$access_map_palette, 
                domain = pull(demo_age_data, !!sym(demo_age_selected())),
                n = 4)
  
})
    
# State map
output$demo2map <- renderLeaflet({
  
  # Map
  demo2map <- demo_age_map_data %>%
    mutate(map_focus = !!sym(demo_age_selected())) %>% 
    leaflet() %>%
    clearShapes() %>%
    addResetMapButton() %>% 
    addPolygons(stroke = TRUE, color = "#444444", weight = 1, smoothFactor = 0, 
                fillColor = ~pal_demo2()(map_focus),
                fillOpacity = 1,
                popup = ~paste(state_name, " (", state_abbv, ")", "<br>",
                               percent(map_focus,
                                       scale = 1, accuracy = 0.1)),
                layerId = ~state_name) %>% 
    addLegend(position = "topright", pal = pal_demo2(),
              values = ~map_focus,
              labFormat =  function(type, cuts, p) {
                n = length(cuts)
                paste0(as.numeric(cuts)[-n], " &ndash; ", as.numeric(cuts)[-1])
              },
              title = paste0("PWD (%),<br>", input$demo_age_type))
  
  demo2map

})

# Click event for the map
click_demo2map <- eventReactive(input$demo2map_shape_click, {
  
  x <- input$demo2map_shape_click
  y <- x$id
  
  return(y)

})

# Add the clicked state to the map, and remove when a new one is clicked
observe({
  
  req(click_demo2map())
  
  demo2map <- leafletProxy("demo2map") %>%
    removeShape("highlight_state") %>%
    addPolygons(data = demo_age_map_data[demo_age_map_data$state_name == click_demo2map(), ], 
                fill = FALSE, weight = 3,
                color = "#00FFFF", opacity = 1, layerId = "highlight_state")
  
})

# Fetch data for the clicked state
demo_age_data_selected <- reactive({
  
  if(is.null(input$demo2map_shape_click)){
    demo_age_data
  } else {
    demo_age_data %>% 
      filter(state_name == click_demo2map())
  }
  
})

leafletOutput("demo2map") 

```

### Table {.wide-DT}

```{r, demographics age table }

# Columns to show
demo_age_cols_selected <- reactive({

if (input$demo_age_type == "18-64"){
  "18_64"
} else {
  "65"
}

})

# Data table
DT::renderDataTable({

  # Table
  DT::datatable(
    demo_age_data_selected() %>%
      rename("percent_pwd_18_64" = percent_people_18_64_with_a_disability,
             "pwd_18_64" = pwd_18_64_years,
             "total_pop_18_64" = total_population18_64,
             "percent_pwd_65+" =percent_people_65_with_a_disability,
             "pwd_65+" = pwd_65_years,
             "total_pop_65+" = total_population65) %>%
      mutate(across(matches("percent"), percent, scale = 1, accuracy = 0.1),
             across(where(is.numeric), comma)) %>%
      select(starts_with("state"), matches(demo_age_cols_selected())),
  options(scrollX = "200px"))

})

```

Row {data-height=100}
-----------------------------------------------------------------------

### {.section-divider}

#### Race

##### Percent of Persons with Disabilities

Row {data-height=500}
-----------------------------------------------------------------------

### Map

```{r, demographics race map}

# Data for this section
demo_race_data <- demographics %>% 
  filter(is.na(city)) %>% 
  select("state_name" = state, "state_abbv" = abbrev, 
         pwd_caucasian:percent_of_pwd_who_are_white_non_hispanic, pwd) %>% 
  mutate(across(starts_with("percent"), round, 1))

# SF data and palette
demo_race_map_data <- demo_race_data %>% 
    left_join(states_sf, ., by = c("state_name", "state_abbv")) %>% 
    st_transform(4326)
  
# Input for column to map
selectInput("demo_race_type", 
            label = "Select a category", 
            choices = c("Caucasian", "African American", "Another Race",
                        "Hispanic", "White, Non-Hispanic"),
            selected = "Caucasian")

demo_race_selected <- reactive({
  
  if (input$demo_race_type == "Caucasian"){
    "percent_of_pwd_who_are_caucasian"
  } else if (input$demo_race_type == "African American"){
    "percent_of_pwd_who_are_black_african_american"
  } else if (input$demo_race_type == "Another Race"){
    "pwd_of_another_race_sum_of_five_columns_to_right"
  } else if (input$demo_race_type == "White, Non-Hispanic"){
    "percent_of_pwd_who_are_white_non_hispanic"
  } else {
    "percent_of_pwd_who_are_hispanic"
  }
  
})

pal_demo3 <- reactive ({ 
    
    colorQuantile(palette = input$access_map_palette, 
                  domain = pull(demo_race_data, !!sym(demo_race_selected())),
                  n = 4)
                 
  })
    
# State map
output$demo3map <- renderLeaflet({
  
  # Map
  demo3map <- demo_race_map_data %>%
    mutate(map_focus = !!sym(demo_race_selected())) %>% 
    leaflet() %>%
    clearShapes() %>%
    addResetMapButton() %>% 
    addPolygons(stroke = TRUE, color = "#444444", weight = 1, smoothFactor = 0, 
                fillColor = ~pal_demo3()(map_focus),
                fillOpacity = 1,
                popup = ~paste(state_name, " (", state_abbv, ")", "<br>",
                               percent(map_focus,
                                       scale = 1, accuracy = 0.1)),
                layerId = ~state_name) %>% 
    addLegend(position = "topright", pal = pal_demo3(),
              values = ~map_focus,
              labFormat =  function(type, cuts, p) {
                n = length(cuts)
                paste0(as.numeric(cuts)[-n], " &ndash; ", as.numeric(cuts)[-1])
              },
              title = paste0("PWD (%),<br>", input$demo_race_type))
  
  demo3map

})

# Click event for the map
click_demo3map <- eventReactive(input$demo3map_shape_click, {
  
  x <- input$demo3map_shape_click
  y <- x$id
  
  return(y)

})

# Add the clicked state to the map, and remove when a new one is clicked
observe({
  
  req(click_demo3map())
  
  demo3map <- leafletProxy("demo3map") %>%
    removeShape("highlight_state") %>%
    addPolygons(data = demo_race_map_data[demo_race_map_data$state_name == click_demo3map(), ], 
                fill = FALSE, weight = 3,
                color = "#00FFFF", opacity = 1, layerId = "highlight_state")
  
})

# Fetch data for the clicked state
demo_race_data_selected <- reactive({
  
  if(is.null(input$demo3map_shape_click)){
    demo_race_data
  } else {
    demo_race_data %>% 
      filter(state_name == click_demo3map())
  }
  
})

leafletOutput("demo3map")  

```

### Table {.wide-DT}

```{r, demographics race table}

# Columns to show
demo_race_cols_selected <- reactive({
  
  if (input$demo_race_type == "Caucasian"){
    "caucasian"
  } else if (input$demo_race_type == "African American"){
    "black"
  } else if (input$demo_race_type == "Another Race"){
    "other_race"
  } else if (input$demo_race_type == "White, Non-Hispanic"){
    "non_hispanic"
  } else {
    "(?<!non_)hispanic"
  }
  
})

# Data table
DT::renderDataTable({
  
  # Table
  DT::datatable(
    demo_race_data_selected() %>%
      rename("percent_pwd_caucasian" = percent_of_pwd_who_are_caucasian, 
             "percent_pwd_black" = percent_of_pwd_who_are_black_african_american,
             "pwd_black" = pwd_black_or_african_american,
             "percent_pwd_other_race" = percent_of_pwd_who_are_of_another_race, 
             "pwd_other_race" = pwd_of_another_race_sum_of_five_columns_to_right,
             "percent_pwd_hispanic" = percent_of_pwd_who_are_hispanic,
             "percent_pwd_white_non_hispanic" = percent_of_pwd_who_are_white_non_hispanic,
             "total_pwd" = pwd) %>% 
      mutate(across(matches("percent"), percent, scale = 1, accuracy = 0.1),
             across(where(is.numeric), comma)) %>% 
      select(starts_with("state"), matches(demo_race_cols_selected(), perl = TRUE)),
  options(scrollX = "200px"))
  
})

```

Row
-----------------------------------------------------------------------

### Racial Composition of Persons with Disabilities, Selected State (Click on Map to Show Chart)

```{r, demographics race plot}

# Plot
renderPlot({
  
  req(click_demo3map())
  
  demo_race_data_selected() %>% 
    select(state_name,
           "Black" = percent_of_pwd_who_are_black_african_american,
           "White, Non-Hispanic" = percent_of_pwd_who_are_white_non_hispanic,
           "Hispanic" = percent_of_pwd_who_are_hispanic,
           "Another Race" = percent_of_pwd_who_are_of_another_race) %>% 
    pivot_longer(cols = Black:`Another Race`,
                 names_to = "Race",
                 values_to = "Percent") %>% 
    mutate(state_name = as_factor(state_name)) %>% 
    ggplot(aes(x = fct_rev(state_name), y = Percent, fill = Race)) +
      geom_bar(stat = "identity", width = 0.5) +
      ylim(0 ,100) +
      labs(x = "State", y = "Percent") +
      coord_flip() +
      ggplot_fill_selected() +
      ggplot_theme_selected() +
      theme(legend.position = "top")
  
})


```

Row {data-height=100}
-----------------------------------------------------------------------

### {.section-divider}

#### Gender

##### Percent of Persons with Disabilities

Row {data-height=500}
-----------------------------------------------------------------------

### Map {data-width=500}

```{r, demographics gender map}

# Data for this section
demo_gender_data <- demographics %>% 
  filter(is.na(city)) %>% 
  select("state_name" = state, "state_abbv" = abbrev, 
         total_male_population:percent_pwd_female, pwd) %>% 
  mutate(across(starts_with("percent"), round, 1))

# SF data and palette
demo_gender_map_data <- demo_gender_data %>% 
    left_join(states_sf, ., by = c("state_name", "state_abbv")) %>% 
    st_transform(4326)
  
# Input for column to map
selectInput("demo_gender_type", 
            label = "Select a category", 
            choices = c("Female", "Male"),
            selected = "Female")

demo_gender_selected <- reactive({
  
  if (input$demo_gender_type == "Female"){
    "percent_of_female_population_with_a_disability"
  } else {
    "percent_of_male_population_with_a_disability"
  }
  
})

pal_demo4 <- reactive ({ 
    
    colorQuantile(palette = input$access_map_palette, 
                  domain = pull(demo_gender_data, !!sym(demo_gender_selected())),
                  n = 4)
                 
  })
    
# State map
output$demo4map <- renderLeaflet({
  
  # Map
  demo4map <- demo_gender_map_data %>%
    mutate(map_focus = !!sym(demo_gender_selected())) %>% 
    leaflet() %>%
    clearShapes() %>%
    addResetMapButton() %>% 
    addPolygons(stroke = TRUE, color = "#444444", weight = 1, smoothFactor = 0, 
                fillColor = ~pal_demo4()(map_focus),
                fillOpacity = 1,
                popup = ~paste(state_name, " (", state_abbv, ")", "<br>",
                               percent(map_focus,
                                       scale = 1, accuracy = 0.1)),
                layerId = ~state_name) %>% 
    addLegend(position = "topright", pal = pal_demo4(),
              values = ~map_focus,
              labFormat =  function(type, cuts, p) {
                n = length(cuts)
                paste0(as.numeric(cuts)[-n], " &ndash; ", as.numeric(cuts)[-1])
              },
              title = paste0("PWD (%),<br>", input$demo_gender_type))
  
  demo4map

})

# Click event for the map
click_demo4map <- eventReactive(input$demo4map_shape_click, {
  
  x <- input$demo4map_shape_click
  y <- x$id
  
  return(y)

})

# Add the clicked state to the map, and remove when a new one is clicked
observe({
  
  req(click_demo4map())
  
  demo4map <- leafletProxy("demo4map") %>%
    removeShape("highlight_state") %>%
    addPolygons(data = demo_gender_map_data[demo_gender_map_data$state_name == click_demo4map(), ], 
                fill = FALSE, weight = 3,
                color = "#00FFFF", opacity = 1, layerId = "highlight_state")
  
})

# Fetch data for the clicked state
demo_gender_data_selected <- reactive({
  
  if(is.null(input$demo4map_shape_click)){
    demo_gender_data
  } else {
    demo_gender_data %>% 
      filter(state_name == click_demo4map())
  }
  
})

leafletOutput("demo4map")  

```

### Table {.wide-DT data-width=500}

```{r, demographics gender table }

# Columns to show
demo_gender_cols_selected <- reactive({
  
  if (input$demo_gender_type == "Female"){
    "female"
  } else {
    "(?<!fe)male"
  }
  
})

# Data table (scroll function for wide data)
DT::renderDataTable({
  
  # Table
  DT::datatable(
    demo_gender_data_selected() %>%
      mutate(across(matches("percent"), percent, scale = 1, accuracy = 0.1),
             across(where(is.numeric), comma)) %>% 
      select(starts_with("state"), matches(demo_gender_cols_selected(), perl = TRUE)),
   options(scrollX = "200px"))
  
})

```

Row {data-height=100}
-----------------------------------------------------------------------

### {.section-divider}

#### Type of Disability

##### Percent of Persons with Disabilities

Row {data-height=500}
-----------------------------------------------------------------------

### Map {data-width=500}

```{r, demographics disability type map}

# Data for this section
demo_distype_data <- demographics %>% 
  filter(is.na(city)) %>% 
  select("state_name" = state, "state_abbv" = abbrev, 
         total_population_2:percent_of_total_population_independent_living_disability, pwd) %>% 
  mutate(across(starts_with("percent"), round, 1))

# SF data and palette
demo_distype_map_data <- demo_distype_data %>% 
    left_join(states_sf, ., by = c("state_name", "state_abbv")) %>% 
    st_transform(4326)
  
# Input for column to map
selectInput("demo_distype_type", 
            label = "Select a category", 
            choices = c("Hearing", "Vision", "Cognitive", 
                        "Ambulatory", "Self Care", "Independent Living"),
            selected = "Hearing")

demo_distype_selected <- reactive({
  
  if (input$demo_distype_type == "Hearing"){
    "percent_of_total_population_hearing_disability"
  } else if (input$demo_distype_type == "Vision"){
    "percent_of_total_population_vision_disability"
  } else if (input$demo_distype_type == "Cognitive"){
    "percent_of_total_population_cognitive_disability"
  } else if (input$demo_distype_type == "Ambulatory"){
    "percent_of_total_population_ambulatory_disability"
  } else if (input$demo_distype_type == "Self Care"){
    "percent_of_total_population_self_care_disability"
  } else {
    "percent_of_total_population_independent_living_disability"
  }
  
})

pal_demo5 <- reactive ({ 
    
    colorQuantile(palette = input$access_map_palette,
                  domain = pull(demo_distype_data, !!sym(demo_distype_selected())),
                  n = 4)
                 
  })
    
# State map
output$demo5map <- renderLeaflet({
  
  # Map
  demo5map <- demo_distype_map_data %>%
    mutate(map_focus = !!sym(demo_distype_selected())) %>% 
    leaflet() %>%
    clearShapes() %>%
    addResetMapButton() %>% 
    addPolygons(stroke = TRUE, color = "#444444", weight = 1, smoothFactor = 0, 
                fillColor = ~pal_demo5()(map_focus),
                fillOpacity = 1,
                popup = ~paste(state_name, " (", state_abbv, ")", "<br>",
                               percent(map_focus,
                                       scale = 1, accuracy = 0.1)),
                layerId = ~state_name) %>% 
    addLegend(position = "topright", pal = pal_demo5(),
              values = ~map_focus,
              labFormat =  function(type, cuts, p) {
                n = length(cuts)
                paste0(as.numeric(cuts)[-n], " &ndash; ", as.numeric(cuts)[-1])
              },
              title = paste0("PWD (%),<br>", input$demo_distype_type))
  
  demo5map

})

# Click event for the map
click_demo5map <- eventReactive(input$demo5map_shape_click, {
  
  x <- input$demo5map_shape_click
  y <- x$id
  
  return(y)

})

# Add the clicked state to the map, and remove when a new one is clicked
observe({
  
  req(click_demo5map())
  
  demo5map <- leafletProxy("demo5map") %>%
    removeShape("highlight_state") %>%
    addPolygons(data = demo_distype_map_data[demo_distype_map_data$state_name == click_demo5map(), ], 
                fill = FALSE, weight = 3,
                color = "#00FFFF", opacity = 1, layerId = "highlight_state")
  
})

# Fetch data for the clicked state
demo_distype_data_selected <- reactive({
  
  if(is.null(input$demo5map_shape_click)){
    demo_distype_data
  } else {
    demo_distype_data %>% 
      filter(state_name == click_demo5map())
  }
  
})

leafletOutput("demo5map")  

```

### Table {.wide-DT data-width=500}

```{r, demographics disability type table }

# Columns to show
demo_distype_cols_selected <- reactive({
  
    if (input$demo_distype_type == "Hearing"){
    "hearing"
  } else if (input$demo_distype_type == "Vision"){
    "vision"
  } else if (input$demo_distype_type == "Cognitive"){
    "cognitive"
  } else if (input$demo_distype_type == "Ambulatory"){
    "ambulatory"
  } else if (input$demo_distype_type == "Self Care"){
    "self_care"
  } else {
    "independent_living"
  }
  
})

# Data table (scroll function for wide data)
DT::renderDataTable({
  
  # Table
  DT::datatable(
    demo_distype_data_selected() %>%
      mutate(across(matches("percent"), percent, scale = 1, accuracy = 0.1),
             across(where(is.numeric), comma)) %>% 
      select(starts_with("state"), matches(demo_distype_cols_selected())),
   options(scrollX = "200px"))
  
})

```



Community Living {data-navmenu="National" data-icon="fa-home"}
======================================================================

Row {data-height=100}
-----------------------------------------------------------------------

### {.section-divider}

#### Where People with Disabilities Live in the Community

##### Percent of Persons with Disabilities

Row {data-height=500}
-----------------------------------------------------------------------

### Map {data-width=500}

```{r, community living where people live map}

# Data for this section
cl_live_data <- community_living %>% 
  select("state_name" = state, "state_abbv" = abbrev, 
         total_population:percent_pwd_other_group_quarters) %>% 
  mutate(across(starts_with("percent"), round, 1)) %>% 
  mutate(pwd_in_home = total_population_pwd - 
           pwd_in_institutionalized_group_quarters -
           pwd_in_non_institutional_group_quarters)

# SF data and palette
cl_live_map_data <- cl_live_data %>% 
    left_join(states_sf, ., by = c("state_name", "state_abbv")) %>% 
    st_transform(4326)
  
# Input for column to map
selectInput("cl_live_type", 
            label = "Select a category", 
            choices = c("Home", "Group Quarters - Institution", "Group Quarters - Other"),
            selected = "Home")

cl_live_selected <- reactive({
  
  if (input$cl_live_type == "Home"){
    "percent_pwd_home"
  } else if (input$cl_live_type == "Group Quarters - Institution"){
    "percent_pwd_institution"
  } else {
    "percent_pwd_other_group_quarters"
  }
  
})

pal_cl1 <- reactive ({ 
    
    colorQuantile(palette = input$access_map_palette, 
                  domain = pull(cl_live_data, !!sym(cl_live_selected())),
                  n = 4)
                 
  })
  
# State map
output$cl1map <- renderLeaflet({
  
  # Map
  cl1map <- cl_live_map_data %>%
    mutate(map_focus = !!sym(cl_live_selected())) %>% 
    leaflet() %>%
    clearShapes() %>%
    addResetMapButton() %>% 
    addPolygons(stroke = TRUE, color = "#444444", weight = 1, smoothFactor = 0, 
                fillColor = ~pal_cl1()(map_focus),
                fillOpacity = 1,
                popup = ~paste(state_name, " (", state_abbv, ")", "<br>",
                               percent(map_focus,
                                       scale = 1, accuracy = 0.1)),
                layerId = ~state_name) %>% 
    addLegend(position = "topright", pal = pal_cl1(),
              values = ~map_focus,
              labFormat =  function(type, cuts, p) {
                n = length(cuts)
                paste0(as.numeric(cuts)[-n], " &ndash; ", as.numeric(cuts)[-1])
              },
              title = paste0("PWD (%),<br>", input$cl_live_type))
  
  cl1map
  
})

# Click event for the map
click_cl1map <- eventReactive(input$cl1map_shape_click, {
  
  x <- input$cl1map_shape_click
  y <- x$id
  
  return(y)

})

# Add the clicked state to the map, and remove when a new one is clicked
observe({
  
  req(click_cl1map())
  
  cl1map <- leafletProxy("cl1map") %>%
    removeShape("highlight_state") %>%
    addPolygons(data = cl_live_map_data[cl_live_map_data$state_name == click_cl1map(), ], 
                fill = FALSE, weight = 3,
                color = "#00FFFF", opacity = 1, layerId = "highlight_state")
  
})

# Fetch data for the clicked state
cl_live_data_selected <- reactive({
  
  if(is.null(input$cl1map_shape_click)){
    cl_live_data
  } else {
    cl_live_data %>% 
      filter(state_name == click_cl1map())
  }
  
})

leafletOutput("cl1map")  

```

### Table {.wide-DT data-width=500}

```{r, community living where people live table }

# Columns to show
cl_live_cols_selected <- reactive({
  
  if (input$cl_live_type == "Home"){
    "home"
  } else if (input$cl_live_type == "Group Quarters - Institution"){
    "(?<!non_)institution"
  } else {
    "(non_institution|other_group_quarters)"
  }
  
})

# Data table (scroll function for wide data)
DT::renderDataTable({
  
  # Table
  DT::datatable(
    cl_live_data_selected() %>%
      mutate(across(matches("percent"), percent, scale = 1, accuracy = 0.1),
             across(where(is.numeric), comma)) %>% 
      select(starts_with("state"), matches(cl_live_cols_selected(), perl = TRUE)),
   options(scrollX = "200px"))
  
})

```

Row {data-height=100}
-----------------------------------------------------------------------

### {.section-divider}

#### Nursing Home Residents

##### Percent of State Residents

Row {data-height=500}
-----------------------------------------------------------------------

### Map {data-width=500}

```{r, community living nursing home map}

# Data for this section
cl_nursing_data <- community_living %>% 
  select("state_name" = state, "state_abbv" = abbrev, 
         total_number_pwd_in_certified_nursing_facilities_2014:institutionalization_rate_per_10_000_people_2014) %>% 
  select(-matches("_2011")) %>% 
  mutate(across(starts_with("percent"), round, 3))

# SF data and palette
cl_nursing_map_data <- cl_nursing_data %>% 
    left_join(states_sf, ., by = c("state_name", "state_abbv")) %>% 
    st_transform(4326)
  
# # Input for column to map
# selectInput("cl_nursing_type", 
#             label = "Select a category", 
#             choices = c("Home", "Group Quarters - Institution", "Group Quarters - Other"),
#             selected = "Home")
# 
cl_nursing_selected <- reactive({ 
  
  "percentage_of_state_residents_in_a_nursing_home_2014_calculated"

#   if (input$cl_nursing_type == "Home"){
#     "percent_pwd_home"
#   } else if (input$cl_nursing_type == "Group Quarters - Institution"){
#     "percent_pwd_institution"
#   } else {
#     "percent_pwd_other_group_quarters"
#   }

})

pal_cl2 <- reactive ({ 
    
    colorQuantile(palette = input$access_map_palette, 
                  domain = pull(cl_nursing_data, !!sym(cl_nursing_selected())),
                  n = 4)
                 
  })
  
# State map
output$cl2map <- renderLeaflet({
  
  # Map
  cl2map <- cl_nursing_map_data %>%
    mutate(map_focus = !!sym(cl_nursing_selected())) %>% 
    leaflet() %>% 
    clearShapes() %>%
    addResetMapButton() %>% 
    addPolygons(stroke = TRUE, color = "#444444", weight = 1, smoothFactor = 0, 
                fillColor = ~pal_cl2()(map_focus),
                fillOpacity = 1,
                popup = ~paste(state_name, " (", state_abbv, ")", "<br>",
                               percent(map_focus,
                                       scale = 1, accuracy = 0.1)),
                layerId = ~state_name) %>% 
    addLegend(position = "topright", pal = pal_cl2(),
              values = ~map_focus,
              labFormat =  function(type, cuts, p) {
                n = length(cuts)
                paste0(as.numeric(cuts)[-n], " &ndash; ", as.numeric(cuts)[-1])
              },
              title = paste0("2014 (%)"))
  
  cl2map
  
})

# Click event for the map
click_cl2map <- eventReactive(input$cl2map_shape_click, {
  
  x <- input$cl2map_shape_click
  y <- x$id
  
  return(y)

})

# Add the clicked state to the map, and remove when a new one is clicked
observe({
  
  req(click_cl2map())
  
  cl2map <- leafletProxy("cl2map") %>%
    removeShape("highlight_state") %>%
    addPolygons(data = cl_nursing_map_data[cl_nursing_map_data$state_name == click_cl2map(), ], 
                fill = FALSE, weight = 3,
                color = "#00FFFF", opacity = 1, layerId = "highlight_state")
  
})

# Fetch data for the clicked state
cl_nursing_data_selected <- reactive({
  
  if(is.null(input$cl2map_shape_click)){
    cl_nursing_data
  } else {
    cl_nursing_data %>% 
      filter(state_name == click_cl2map())
  }
  
})

leafletOutput("cl2map")  

```

### Table {.wide-DT data-width=500}

```{r, community living nursing home table }

# Columns to show
# cl_nursing_cols_selected <- reactive({
#   
#   if (input$cl_nursing_type == "Home"){
#     "home"
#   } else if (input$cl_nursing_type == "Group Quarters - Institution"){
#     "(?<!non_)institution"
#   } else {
#     "(non_institution|other_group_quarters)"
#   }
#   
# })

# Data table (scroll function for wide data)
DT::renderDataTable({
  
  # Table
  DT::datatable(
    cl_nursing_data_selected() %>%
      mutate(across(matches("percent"), percent, scale = 1, accuracy = 0.1),
             across(where(is.numeric), comma)),
      # select(starts_with("state"), matches(cl_nursing_cols_selected(), perl = TRUE)),
   options(scrollX = "200px"))
  
})

```

Row {data-height=100}
-----------------------------------------------------------------------

### {.section-divider}

#### Programs and Spending for Community Living

##### Per State Residents

Row {data-height=500}
-----------------------------------------------------------------------

### Map {data-width=500}

```{r, community living programs spending map}

# Data for this section
cl_ps_data <- community_living %>% 
  select("state_name" = state, "state_abbv" = abbrev, 
         ratio_hcbs_participants_to_total_ltss:mfp_transitions_since_inception_per_10_000_people) %>% 
  mutate(across(starts_with("percent"), round, 1))

# SF data and palette
cl_ps_map_data <- cl_ps_data %>% 
    left_join(states_sf, ., by = c("state_name", "state_abbv")) %>% 
    st_transform(4326)
  
# Input for column to map
selectInput("cl_ps_type", 
            label = "Select a category", 
            choices = c("HCBS", "MFP"),
            selected = "HCBS")

cl_ps_selected <- reactive({
  
  if (input$cl_ps_type == "HCBS"){
    "hcbs_waiver_waitlist_per_10_000_people"
  } else {
    "mfp_transitions_since_inception_per_10_000_people"
  }
  
})

pal_cl3 <- reactive ({ 
    
    colorQuantile(palette = input$access_map_palette, 
                  domain = pull(cl_ps_data, !!sym(cl_ps_selected())),
                  n = 4)
                 
  })
  
# State map
output$cl3map <- renderLeaflet({
  
  # Map
  cl3map <- cl_ps_map_data %>% 
    mutate(map_focus = !!sym(cl_ps_selected())) %>% 
    leaflet() %>%
    clearShapes() %>%
    addResetMapButton() %>% 
    addPolygons(stroke = TRUE, color = "#444444", weight = 1, smoothFactor = 0, 
                fillColor = ~pal_cl3()(map_focus),
                fillOpacity = 1,
                popup = ~paste(state_name, " (", state_abbv, ")", "<br>",
                               round(map_focus, 2)),
                layerId = ~state_name) %>% 
    addLegend(position = "topright", pal = pal_cl3(),
              values = ~map_focus,
              labFormat =  function(type, cuts, p) {
                n = length(cuts)
                paste0(as.numeric(cuts)[-n], " &ndash; ", as.numeric(cuts)[-1])
              },
              title = paste0("Per 10K People,<br>", input$cl_ps_type))
  
  cl3map
  
})

# Click event for the map
click_cl3map <- eventReactive(input$cl3map_shape_click, {
  
  x <- input$cl3map_shape_click
  y <- x$id
  
  return(y)

})

# Add the clicked state to the map, and remove when a new one is clicked
observe({
  
  req(click_cl3map())
  
  cl3map <- leafletProxy("cl3map") %>%
    removeShape("highlight_state") %>%
    addPolygons(data = cl_ps_map_data[cl_ps_map_data$state_name == click_cl3map(), ], 
                fill = FALSE, weight = 3,
                color = "#00FFFF", opacity = 1, layerId = "highlight_state")
  
})

# Fetch data for the clicked state
cl_ps_data_selected <- reactive({
  
  if(is.null(input$cl3map_shape_click)){
    cl_ps_data
  } else {
    cl_ps_data %>% 
      filter(state_name == click_cl3map())
  }
  
})

leafletOutput("cl3map")  

```

### Table {.wide-DT data-width=500}

```{r, community living programs spending table }

# Columns to show
cl_ps_cols_selected <- reactive({
  
  if (input$cl_ps_type == "HCBS"){
    "hcbs"
  } else {
    "mfp"
  }
  
})

# Data table (scroll function for wide data)
DT::renderDataTable({
  
  # Table
  DT::datatable(
    cl_ps_data_selected() %>%
      mutate(across(matches("percent"), percent, scale = 1, accuracy = 0.1),
             across(matches("_per_"), round, 2),
             across(where(is.numeric) & !matches("_per_"), comma)) %>% 
      select(starts_with("state"), matches(cl_ps_cols_selected())),
   options(scrollX = "200px"))
  
})

```



Community Participation {data-navmenu="National" data-icon="fa-group"}
======================================================================

Row {data-height=100}
-----------------------------------------------------------------------

### {.section-divider}

#### Health Coverage

##### Percent of Persons with or without Disabilities

Row {data-height=500}
-----------------------------------------------------------------------

### Map {data-width=500}

```{r, community participation health insurance map}

# Data for this section
cp_insurance_data <- community_participation %>% 
  filter(is.na(city)) %>% 
  select("state_name" = state, "state_abbv" = abbrev, 
         tot_pop_19_64:percent_people_enrolled_in_medicaid_pwod_kff_acs) %>% 
  mutate(across(starts_with("percent"), round, 1))

# SF data and palette
cp_insurance_map_data <- cp_insurance_data %>% 
    left_join(states_sf, ., by = c("state_name", "state_abbv")) %>% 
    st_transform(4326)
  
# Input for column to map
selectInput("cp_insurance_type", 
            label = "Select a category", 
            choices = c("PWD // 19-64 // Private Health Insurance",
                        "PWD // 19-64 // No Health Insurance",
                        "PWD // 65+ // Private Health Insurance",
                        "PWD // 65+ // No Health Insurance",
                        "PWD // Enrolled in Medicare Part A and/or B",
                        "PWD // Enrolled in Medicaid",
                        "PWOD // 19-64 // Private Health Insurance",
                        "PWOD // 19-64 // No Health Insurance",
                        "PWOD // 65+ // Private Health Insurance",
                        "PWOD // 65+ // No Health Insurance",
                        "PWOD // Enrolled in Medicare Part A and/or B",
                        "PWOD // Enrolled in Medicaid"),
            selected = "PWD // 19-64 // Private Health Insurance",
            width = "400px")

cp_insurance_selected <- reactive({
  
  if (input$cp_insurance_type == "PWD // 19-64 // Private Health Insurance"){
    "percent_pwd_19_64_private_health_insurance"
  } else if (input$cp_insurance_type == "PWD // 19-64 // No Health Insurance"){
    "percent_pwd_19_64_no_health_insurance"
  } else if (input$cp_insurance_type == "PWD // 65+ // Private Health Insurance"){
    "percent_pwd_65_private_health_insurance"
  } else if (input$cp_insurance_type == "PWD // 65+ // No Health Insurance"){
    "percent_pwd_65_no_health_insurance"
  } else if (input$cp_insurance_type == "PWD // Enrolled in Medicare Part A and/or B"){
    "percent_people_enrolled_in_medicare_part_a_and_or_b_pwd_2017_cms_acs"
  } else if (input$cp_insurance_type == "PWD // Enrolled in Medicaid"){
    "percent_people_enrolled_in_medicaid_pwd_kff_acs"
  } else if (input$cp_insurance_type == "PWOD // 19-64 // Private Health Insurance"){
    "percent_pwod_19_64_private_health_insurance"
  } else if (input$cp_insurance_type == "PWOD // 19-64 // No Health Insurance"){
    "percent_pwod_19_64_no_health_insurance"
  } else if (input$cp_insurance_type == "PWOD // 65+ // Private Health Insurance"){
    "percent_pwod_65_private_health_insurance"
  } else if (input$cp_insurance_type == "PWOD // 65+ // No Health Insurance"){
    "percent_pwod_65_no_health_insurance"
  } else if (input$cp_insurance_type == "PWOD // Enrolled in Medicare Part A and/or B"){
    "percent_people_enrolled_in_medicare_part_a_and_or_b_pwod_2017_cms_acs"
  } else {
    "percent_people_enrolled_in_medicaid_pwod_kff_acs"
  }
  
})

pal_cp1 <- reactive ({ 
    
    colorQuantile(palette = input$access_map_palette, 
                  domain = pull(cp_insurance_data, !!sym(cp_insurance_selected())),
                  n = 4)
                 
  })
  
# State map
output$cp1map <- renderLeaflet({
  
  # Map
  cp1map <- cp_insurance_map_data %>%
    mutate(map_focus = !!sym(cp_insurance_selected())) %>% 
    leaflet() %>%
    clearShapes() %>%
    addResetMapButton() %>% 
    addPolygons(stroke = TRUE, color = "#444444", weight = 1, smoothFactor = 0, 
                fillColor = ~pal_cp1()(map_focus),
                fillOpacity = 1,
                popup = ~paste(state_name, " (", state_abbv, ")", "<br>",
                               percent(map_focus,
                                       scale = 1, accuracy = 0.1)),
                layerId = ~state_name) %>% 
    addLegend(position = "topright", pal = pal_cp1(),
              values = ~map_focus,
              labFormat =  function(type, cuts, p) {
                n = length(cuts)
                paste0(as.numeric(cuts)[-n], " &ndash; ", as.numeric(cuts)[-1])
              },
              title = paste0(str_replace_all(input$cp_insurance_type,
                                             " // ", "<br>"),
                             " (%)"))
  
  cp1map
  
})

# Click event for the map
click_cp1map <- eventReactive(input$cp1map_shape_click, {
  
  x <- input$cp1map_shape_click
  y <- x$id
  
  return(y)

})

# Add the clicked state to the map, and remove when a new one is clicked
observe({
  
  req(click_cp1map())
  
  cp1map <- leafletProxy("cp1map") %>%
    removeShape("highlight_state") %>%
    addPolygons(data = cp_insurance_map_data[cp_insurance_map_data$state_name == click_cp1map(), ], 
                fill = FALSE, weight = 3,
                color = "#00FFFF", opacity = 1, layerId = "highlight_state")
  
})

# Fetch data for the clicked state
cp_insurance_data_selected <- reactive({
  
  if(is.null(input$cp1map_shape_click)){
    cp_insurance_data
  } else {
    cp_insurance_data %>% 
      filter(state_name == click_cp1map())
  }
  
})

leafletOutput("cp1map")  

```

### Table {.wide-DT data-width=500}

```{r, community participation health insurance table }

# Columns to show
cp_insurance_cols_selected <- reactive({
             
  if (input$cp_insurance_type == "PWD // 19-64 // Private Health Insurance"){
    "pwd.*19_64.*private_health_insurance"
  } else if (input$cp_insurance_type == "PWD // 19-64 // No Health Insurance"){
    "pwd.*19_64.*no_health_insurance"
  } else if (input$cp_insurance_type == "PWD // 65+ // Private Health Insurance"){
    "pwd.*65.*private_health_insurance"
  } else if (input$cp_insurance_type == "PWD // 65+ // No Health Insurance"){
    "pwd.*65.*no_health_insurance"
  } else if (input$cp_insurance_type == "PWD // Enrolled in Medicare Part A and/or B"){
    "pwd.*medicare"
  } else if (input$cp_insurance_type == "PWD // Enrolled in Medicaid"){
    "pwd.*medicaid"
  } else if (input$cp_insurance_type == "PWOD // 19-64 // Private Health Insurance"){
    "pwod.*19_64.*private_health_insurance"
  } else if (input$cp_insurance_type == "PWOD // 19-64 // No Health Insurance"){
    "pwod.*19_64.*no_health_insurance"
  } else if (input$cp_insurance_type == "PWOD // 65+ // Private Health Insurance"){
    "pwod.*65.*private_health_insurance"
  } else if (input$cp_insurance_type == "PWOD // 65+ // No Health Insurance"){
    "pwod.*65.*no_health_insurance"
  } else if (input$cp_insurance_type == "PWOD // Enrolled in Medicare Part A and/or B"){
    "pwod.*medicare"
  } else {
    "pwod.*medicaid"
  }
  
})

# Data table (scroll function for wide data)
DT::renderDataTable({
  
  # Table
  DT::datatable(
    cp_insurance_data_selected() %>%
      mutate(across(matches("percent"), percent, scale = 1, accuracy = 0.1),
             across(where(is.numeric), comma)) %>% 
      select(starts_with("state"), matches(cp_insurance_cols_selected(), perl = TRUE)),
   options(scrollX = "200px"))
  
})

```

Row {data-height=100}
-----------------------------------------------------------------------

### {.section-divider}

#### Community Based Subsidized Housing

##### Percent of Residents or Households with Disability

Row {data-height=500}
-----------------------------------------------------------------------

### Map {data-width=500}

```{r, community participation housing map}

# Data for this section
cp_housing_data <- community_participation %>% 
  filter(is.na(city)) %>% 
  select("state_name" = state, "state_abbv" = abbrev, 
         percent_of_households_in_public_housing_with_residents_that_are_disabled_hud_picture_2019:percent_of_households_with_a_tenant_based_voucher_that_have_a_disabled_resident_09_1_18_12_31_19) %>% 
  mutate(across(starts_with("percent"), round, 1))

# SF data and palette
cp_housing_map_data <- cp_housing_data %>% 
    left_join(states_sf, ., by = c("state_name", "state_abbv")) %>% 
    st_transform(4326)
  
# Input for column to map
selectInput("cp_housing_type", 
            label = "Select a category", 
            choices = c("Residents in Public Housing with a Disability",
                        "Residents with a Housing Choice Voucher (Section 8) with a Disability",
                        "Households in Public Housing with a Resident who has a Disability",
                        "Households with a Housing Choice Voucher with a Resident who has a Disability"),
            selected = "Residents in Public Housing with a Disability",
            width = "400px")

cp_housing_selected <- reactive({
  
  if (input$cp_housing_type == "Residents in Public Housing with a Disability"){
    "percent_of_households_in_public_housing_with_residents_that_are_disabled_hud_picture_2019"
  } else if (input$cp_housing_type == "Residents with a Housing Choice Voucher (Section 8) with a Disability"){
    "percent_residents_with_housing_choice_vouchers_who_are_disabled_hud_picture_2018"
  } else if (input$cp_housing_type == "Households in Public Housing with a Resident who has a Disability"){
    "percent_households_in_public_housing_that_have_a_disabled_resident_09_1_18_12_31_19"
  } else {
    "percent_of_households_with_a_tenant_based_voucher_that_have_a_disabled_resident_09_1_18_12_31_19"
  }
  
})

pal_cp2 <- reactive ({ 
    
    colorQuantile(palette = input$access_map_palette, 
                  domain = pull(cp_housing_data, !!sym(cp_housing_selected())),
                  n = 4)
                 
  })
  
# State map
output$cp2map <- renderLeaflet({
  
  # Map
  cp2map <- cp_housing_map_data %>%
    mutate(map_focus = !!sym(cp_housing_selected())) %>% 
    leaflet() %>%
    clearShapes() %>%
    addResetMapButton() %>% 
    addPolygons(stroke = TRUE, color = "#444444", weight = 1, smoothFactor = 0, 
                fillColor = ~pal_cp2()(map_focus),
                fillOpacity = 1,
                popup = ~paste(state_name, " (", state_abbv, ")", "<br>",
                               percent(map_focus,
                                       scale = 1, accuracy = 0.1)),
                layerId = ~state_name) %>% 
    addLegend(position = "topright", pal = pal_cp2(),
              values = ~map_focus,
              labFormat =  function(type, cuts, p) {
                n = length(cuts)
                paste0(as.numeric(cuts)[-n], " &ndash; ", as.numeric(cuts)[-1])
              },
              title = paste0(str_replace_all(input$cp_housing_type,
                                             " // ", "<br>"),
                             " (%)"))
  
  cp2map
  
})

# Click event for the map
click_cp2map <- eventReactive(input$cp2map_shape_click, {
  
  x <- input$cp2map_shape_click
  y <- x$id
  
  return(y)

})

# Add the clicked state to the map, and remove when a new one is clicked
observe({
  
  req(click_cp2map())
  
  cp2map <- leafletProxy("cp2map") %>%
    removeShape("highlight_state") %>%
    addPolygons(data = cp_housing_map_data[cp_housing_map_data$state_name == click_cp2map(), ], 
                fill = FALSE, weight = 3,
                color = "#00FFFF", opacity = 1, layerId = "highlight_state")
  
})

# Fetch data for the clicked state
cp_housing_data_selected <- reactive({
  
  if(is.null(input$cp2map_shape_click)){
    cp_housing_data
  } else {
    cp_housing_data %>% 
      filter(state_name == click_cp2map())
  }
  
})

leafletOutput("cp2map")  

```

### Table {.wide-DT data-width=500}

```{r, community participation housing table }

# Columns to show
cp_housing_cols_selected <- reactive({
             
  if (input$cp_housing_type == "Residents in Public Housing with a Disability"){
    "public_housing.*residents"
  } else if (input$cp_housing_type == "Residents with a Housing Choice Voucher (Section 8) with a Disability"){
    "residents.*housing_choice_voucher"
  } else if (input$cp_housing_type == "Households in Public Housing with a Resident who has a Disability"){
    "public_housing.*disabled_resident"
  } else {
    "voucher.*disabled_resident"
  }
  
})

# Data table (scroll function for wide data)
DT::renderDataTable({
  
  # Table
  DT::datatable(
    cp_housing_data_selected() %>%
      mutate(across(matches("percent"), percent, scale = 1, accuracy = 0.1),
             across(where(is.numeric), comma)) %>% 
      select(starts_with("state"), matches(cp_housing_cols_selected(), perl = TRUE)),
   options(scrollX = "200px"))
  
})

```

Row {data-height=100}
-----------------------------------------------------------------------

### {.section-divider}

#### Transit Usage - Commuting

##### Percent of Persons with or without Disabilities

Row {data-height=500}
-----------------------------------------------------------------------

### Map {data-width=500}

```{r, community participation transit map}

# Data for this section
cp_transit_data <- community_participation %>% 
  filter(is.na(city)) %>% 
  select("state_name" = state, "state_abbv" = abbrev, 
         percent_pwd_that_commute_to_work_by_public_transit_age_16:percent_pwod_that_commute_to_work_by_car_drove_alone_age_16) %>% 
  mutate(across(starts_with("percent"), round, 1))

# SF data and palette
cp_transit_map_data <- cp_transit_data %>% 
    left_join(states_sf, ., by = c("state_name", "state_abbv")) %>% 
    st_transform(4326)
  
# Input for column to map
selectInput("cp_transit_type", 
            label = "Select a category", 
            choices = c("PWD // Public Transit",
                        "PWD // Drive Alone",
                        "PWOD // Public Transit",
                        "PWOD // Drive Alone"),
            selected = "PWD // Public Transit",
            width = "400px")

cp_transit_selected <- reactive({
  
  if (input$cp_transit_type == "PWD // Public Transit"){
    "percent_pwd_that_commute_to_work_by_public_transit_age_16"
  } else if (input$cp_transit_type == "PWD // Drive Alone"){
    "percent_pwd_that_commute_to_work_by_car_drove_alone_age_16"
  } else if (input$cp_transit_type == "PWOD // Public Transit"){
    "percent_pwod_that_commute_to_work_by_public_transit_age_16"
  } else {
    "percent_pwod_that_commute_to_work_by_car_drove_alone_age_16"
  }
  
})

pal_cp3 <- reactive ({ 
    
    colorQuantile(palette = input$access_map_palette, 
                  domain = pull(cp_transit_data, !!sym(cp_transit_selected())),
                  n = 4)
                 
  })
  
# State map
output$cp3map <- renderLeaflet({
  
  # Map
  cp3map <- cp_transit_map_data %>%
    mutate(map_focus = !!sym(cp_transit_selected())) %>% 
    leaflet() %>%
    clearShapes() %>%
    addResetMapButton() %>% 
    addPolygons(stroke = TRUE, color = "#444444", weight = 1, smoothFactor = 0, 
                fillColor = ~pal_cp3()(map_focus),
                fillOpacity = 1,
                popup = ~paste(state_name, " (", state_abbv, ")", "<br>",
                               percent(map_focus,
                                       scale = 1, accuracy = 0.1)),
                layerId = ~state_name) %>% 
    addLegend(position = "topright", pal = pal_cp3(),
              values = ~map_focus,
              labFormat =  function(type, cuts, p) {
                n = length(cuts)
                paste0(as.numeric(cuts)[-n], " &ndash; ", as.numeric(cuts)[-1])
              },
              title = paste0(str_replace_all(input$cp_transit_type,
                                             " // ", "<br>"),
                             " (%)"))
  
  cp3map
  
})

# Click event for the map
click_cp3map <- eventReactive(input$cp3map_shape_click, {
  
  x <- input$cp3map_shape_click
  y <- x$id
  
  return(y)

})

# Add the clicked state to the map, and remove when a new one is clicked
observe({
  
  req(click_cp3map())
  
  cp3map <- leafletProxy("cp3map") %>%
    removeShape("highlight_state") %>%
    addPolygons(data = cp_transit_map_data[cp_transit_map_data$state_name == click_cp3map(), ], 
                fill = FALSE, weight = 3,
                color = "#00FFFF", opacity = 1, layerId = "highlight_state")
  
})

# Fetch data for the clicked state
cp_transit_data_selected <- reactive({
  
  if(is.null(input$cp3map_shape_click)){
    cp_transit_data
  } else {
    cp_transit_data %>% 
      filter(state_name == click_cp3map())
  }
  
})

leafletOutput("cp3map")  

```

### Table {.wide-DT data-width=500}

```{r, community participation transit table }

# Columns to show
cp_transit_cols_selected <- reactive({
             
  if (input$cp_transit_type == "PWD // Public Transit"){
    "pwd.*transit"
  } else if (input$cp_transit_type == "PWD // Drive Alone"){
    "pwd.*drove_alone"
  } else if (input$cp_transit_type == "PWOD // Public Transit"){
    "pwod.*transit"
  } else {
    "pwod.*drove_alone"
  }
  
})

# Data table (scroll function for wide data)
DT::renderDataTable({
  
  # Table
  DT::datatable(
    cp_transit_data_selected() %>%
      mutate(across(matches("percent"), percent, scale = 1, accuracy = 0.1),
             across(where(is.numeric), comma)) %>% 
      select(starts_with("state"), matches(cp_transit_cols_selected(), perl = TRUE)),
   options(scrollX = "200px"))
  
})

```

Row {data-height=100}
-----------------------------------------------------------------------

### {.section-divider}

#### Crime

##### Per 10,000 People

Row {data-height=500}
-----------------------------------------------------------------------

```{r, community participation crime map}

# Data for this section
cp_crime_data <- community_participation %>% 
  filter(is.na(city)) %>% 
  select("state_name" = state, "state_abbv" = abbrev, 
         total_population:number_of_violent_crimes_per_10_000_people) %>% 
  mutate(across(starts_with("percent"), round, 1))

# SF data and palette
cp_crime_map_data <- cp_crime_data %>% 
    left_join(states_sf, ., by = c("state_name", "state_abbv")) %>% 
    st_transform(4326)
  
# Input for column to map
selectInput("cp_crime_type", 
            label = "Select a category", 
            choices = c("Property",
                        "Violent"),
            selected = "Property",
            width = "400px")

cp_crime_selected <- reactive({
  
  if (input$cp_crime_type == "Property"){
    "number_of_property_crimes_per_10_000_people"
  } else {
    "number_of_violent_crimes_per_10_000_people"
  }
  
})

pal_cp4 <- reactive ({ 
    
    colorQuantile(palette = input$access_map_palette, 
                  domain = pull(cp_crime_data, !!sym(cp_crime_selected())),
                  n = 4)
                 
  })
  
# State map
output$cp4map <- renderLeaflet({
  
  # Map
  cp4map <- cp_crime_map_data %>%
    mutate(map_focus = !!sym(cp_crime_selected())) %>% 
    leaflet() %>%
    clearShapes() %>%
    addResetMapButton() %>% 
    addPolygons(stroke = TRUE, color = "#444444", weight = 1, smoothFactor = 0, 
                fillColor = ~pal_cp4()(map_focus),
                fillOpacity = 1,
                popup = ~paste(state_name, " (", state_abbv, ")", "<br>",
                               percent(map_focus,
                                       scale = 1, accuracy = 0.1)),
                layerId = ~state_name) %>% 
    addLegend(position = "topright", pal = pal_cp4(),
              values = ~map_focus,
              labFormat =  function(type, cuts, p) {
                n = length(cuts)
                paste0(as.numeric(cuts)[-n], " &ndash; ", as.numeric(cuts)[-1])
              },
              title = paste0(str_replace_all(input$cp_crime_type,
                                             " // ", "<br>"),
                             " (%)"))
  
  cp4map
  
})

# Click event for the map
click_cp4map <- eventReactive(input$cp4map_shape_click, {
  
  x <- input$cp4map_shape_click
  y <- x$id
  
  return(y)

})

# Add the clicked state to the map, and remove when a new one is clicked
observe({
  
  req(click_cp4map())
  
  cp4map <- leafletProxy("cp4map") %>%
    removeShape("highlight_state") %>%
    addPolygons(data = cp_crime_map_data[cp_crime_map_data$state_name == click_cp4map(), ], 
                fill = FALSE, weight = 3,
                color = "#00FFFF", opacity = 1, layerId = "highlight_state")
  
})

# Fetch data for the clicked state
cp_crime_data_selected <- reactive({
  
  if(is.null(input$cp4map_shape_click)){
    cp_crime_data
  } else {
    cp_crime_data %>% 
      filter(state_name == click_cp4map())
  }
  
})

leafletOutput("cp4map")  

```

### Table {.wide-DT data-width=500}

```{r, community participation crime table }

# Columns to show
cp_crime_cols_selected <- reactive({
             
  if (input$cp_crime_type == "Property"){
    "property"
  } else {
    "violent"
  }
  
})

# Data table (scroll function for wide data)
DT::renderDataTable({
  
  # Table
  DT::datatable(
    cp_crime_data_selected() %>%
      mutate(across(matches("percent"), percent, scale = 1, accuracy = 0.1),
             across(where(is.numeric), comma)) %>% 
      select(starts_with("state"), matches(cp_crime_cols_selected(), perl = TRUE)),
   options(scrollX = "200px"))
  
})

```

Row {data-height=100}
-----------------------------------------------------------------------

### {.section-divider}

#### Educational Attainment

##### Percent of Persons with or without Disabilities

Row {data-height=500}
-----------------------------------------------------------------------

### Map {data-width=500}

```{r, community participation education map}

# Data for this section
cp_education_data <- community_participation %>% 
  filter(is.na(city)) %>% 
  select("state_name" = state, "state_abbv" = abbrev, 
         percent_pwd_less_than_high_school_age_25:percent_pwod_bachelors_degree_or_higher_age_25) %>% 
  mutate(across(starts_with("percent"), round, 1))

# SF data and palette
cp_education_map_data <- cp_education_data %>% 
    left_join(states_sf, ., by = c("state_name", "state_abbv")) %>% 
    st_transform(4326)
  
# Input for column to map
selectInput("cp_education_type", 
            label = "Select a category", 
            choices = c("PWD // Less Than High School",
                        "PWD // HS or GED",
                        "PWD // Associate's Degree",
                        "PWD // Bachelor's Degree or Higher",
                        "PWOD // Less Than High School",
                        "PWOD // HS or GED",
                        "PWOD // Associate's Degree",
                        "PWOD // Bachelor's Degree or Higher"),
            selected = "PWD // Less Than High School",
            width = "400px")

cp_education_selected <- reactive({
  
  if (input$cp_education_type == "PWD // Less Than High School"){
    "percent_pwd_less_than_high_school_age_25"
  } else if (input$cp_education_type == "PWD // HS or GED"){
    "percent_pwd_hs_or_ged_age_25"
  } else if (input$cp_education_type == "PWD // Associate's Degree"){
    "percent_pwd_college_or_assoc_degree_age_25"
  } else if (input$cp_education_type == "PWD // Bachelor's Degree or Higher"){
    "percent_pwd_bachelors_degree_or_higher_age_25"
  } else if (input$cp_education_type == "PWOD // Less Than High School"){
    "percent_pwod_less_than_high_school_age_25"
  } else if (input$cp_education_type == "PWOD // HS or GED"){
    "percent_pwod_hs_or_ged_age_25"
  } else if (input$cp_education_type == "PWOD // Associate's Degree"){
    "percent_pwod_college_or_assoc_degree_age_25"
  } else {
    "percent_pwod_bachelors_degree_or_higher_age_25"
  }
  
})

pal_cp5 <- reactive ({ 
    
    colorQuantile(palette = input$access_map_palette, 
                  domain = pull(cp_education_data, !!sym(cp_education_selected())),
                  n = 4)
                 
  })
  
# State map
output$cp5map <- renderLeaflet({
  
  # Map
  cp5map <- cp_education_map_data %>%
    mutate(map_focus = !!sym(cp_education_selected())) %>% 
    leaflet() %>%
    clearShapes() %>%
    addResetMapButton() %>% 
    addPolygons(stroke = TRUE, color = "#444444", weight = 1, smoothFactor = 0, 
                fillColor = ~pal_cp5()(map_focus),
                fillOpacity = 1,
                popup = ~paste(state_name, " (", state_abbv, ")", "<br>",
                               percent(map_focus,
                                       scale = 1, accuracy = 0.1)),
                layerId = ~state_name) %>% 
    addLegend(position = "topright", pal = pal_cp5(),
              values = ~map_focus,
              labFormat =  function(type, cuts, p) {
                n = length(cuts)
                paste0(as.numeric(cuts)[-n], " &ndash; ", as.numeric(cuts)[-1])
              },
              title = paste0(str_replace_all(input$cp_education_type,
                                             " // ", "<br>"),
                             " (%)"))
  
  cp5map
  
})

# Click event for the map
click_cp5map <- eventReactive(input$cp5map_shape_click, {
  
  x <- input$cp5map_shape_click
  y <- x$id
  
  return(y)

})

# Add the clicked state to the map, and remove when a new one is clicked
observe({
  
  req(click_cp5map())
  
  cp5map <- leafletProxy("cp5map") %>%
    removeShape("highlight_state") %>%
    addPolygons(data = cp_education_map_data[cp_education_map_data$state_name == click_cp5map(), ], 
                fill = FALSE, weight = 3,
                color = "#00FFFF", opacity = 1, layerId = "highlight_state")
  
})

# Fetch data for the clicked state
cp_education_data_selected <- reactive({
  
  if(is.null(input$cp5map_shape_click)){
    cp_education_data
  } else {
    cp_education_data %>% 
      filter(state_name == click_cp5map())
  }
  
})

leafletOutput("cp5map")  

```

### Table {.wide-DT data-width=500}

```{r, community participation education table }

# Columns to show
cp_education_cols_selected <- reactive({
             
  if (input$cp_education_type == "PWD // Less Than High School"){
    "pwd.*less_than_high_school"
  } else if (input$cp_education_type == "PWD // HS or GED"){
    "pwd.*hs_or_ged"
  } else if (input$cp_education_type == "PWD // Associate's Degree"){
    "pwd.*college_or_assoc"
  } else if (input$cp_education_type == "PWD // Bachelor's Degree or Higher"){
    "pwd.*bachelors"
  } else if (input$cp_education_type == "PWOD // Less Than High School"){
    "pwod.*less_than_high_school"
  } else if (input$cp_education_type == "PWOD // HS or GED"){
    "pwod.*hs_or_ged"
  } else if (input$cp_education_type == "PWOD // Associate's Degree"){
    "pwod.*college_or_assoc"
  } else {
    "pwod.*bachelors"
  }
  
})

# Data table (scroll function for wide data)
DT::renderDataTable({
  
  # Table
  DT::datatable(
    cp_education_data_selected() %>%
      mutate(across(matches("percent"), percent, scale = 1, accuracy = 0.1),
             across(where(is.numeric), comma)) %>% 
      select(starts_with("state"), matches(cp_education_cols_selected(), perl = TRUE)),
   options(scrollX = "200px"))
  
})

```

Row {data-height=100}
-----------------------------------------------------------------------

### {.section-divider}

#### Voter Turnout

##### Percent of Persons with or without Disabilities

Row {data-height=500}
-----------------------------------------------------------------------

### Map {data-width=500}

```{r, community participation voting map}

# Data for this section
cp_voting_data <- community_participation %>% 
  filter(is.na(city)) %>% 
  select("state_name" = state, "state_abbv" = abbrev, 
         pwd_voter_turnout_2012:change_in_disability_gap) %>% 
  mutate(across(starts_with("percent"), round, 1))

# SF data and palette
cp_voting_map_data <- cp_voting_data %>% 
    left_join(states_sf, ., by = c("state_name", "state_abbv")) %>% 
    st_transform(4326)
  
# Input for column to map
selectInput("cp_voting_type", 
            label = "Select a category", 
            choices = c("PWD // Voter Turnout (2018)",
                        "PWOD // Voter Turnout (2018)",
                        "Disability Gap (2018)"),
            selected = "PWD // Voter Turnout (2018)",
            width = "400px")

cp_voting_selected <- reactive({
  
  if (input$cp_voting_type == "PWD // Voter Turnout (2018)"){
    "pwd_voter_turnout_2018"
  } else if (input$cp_voting_type == "PWOD // Voter Turnout (2018)"){
    "pwod_voter_turnout_2018"
  } else {
    "disability_gap_2018"
  }
  
})

pal_cp6 <- reactive ({ 
    
    colorQuantile(palette = input$access_map_palette, 
                  domain = pull(cp_voting_data, !!sym(cp_voting_selected())),
                  n = 4)
                 
  })
  
# State map
output$cp6map <- renderLeaflet({
  
  # Map
  cp6map <- cp_voting_map_data %>%
    mutate(map_focus = !!sym(cp_voting_selected())) %>% 
    leaflet() %>%
    clearShapes() %>%
    addResetMapButton() %>% 
    addPolygons(stroke = TRUE, color = "#444444", weight = 1, smoothFactor = 0, 
                fillColor = ~pal_cp6()(map_focus),
                fillOpacity = 1,
                popup = ~paste(state_name, " (", state_abbv, ")", "<br>",
                               percent(map_focus,
                                       scale = 1, accuracy = 0.1)),
                layerId = ~state_name) %>% 
    addLegend(position = "topright", pal = pal_cp6(),
              values = ~map_focus,
              labFormat =  function(type, cuts, p) {
                n = length(cuts)
                paste0(as.numeric(cuts)[-n], " &ndash; ", as.numeric(cuts)[-1])
              },
              title = paste0(str_replace_all(input$cp_voting_type,
                                             " // ", "<br>"),
                             " (%)"))
  
  cp6map
  
})

# Click event for the map
click_cp6map <- eventReactive(input$cp6map_shape_click, {
  
  x <- input$cp6map_shape_click
  y <- x$id
  
  return(y)

})

# Add the clicked state to the map, and remove when a new one is clicked
observe({
  
  req(click_cp6map())
  
  cp6map <- leafletProxy("cp6map") %>%
    removeShape("highlight_state") %>%
    addPolygons(data = cp_voting_map_data[cp_voting_map_data$state_name == click_cp6map(), ], 
                fill = FALSE, weight = 3,
                color = "#00FFFF", opacity = 1, layerId = "highlight_state")
  
})

# Fetch data for the clicked state
cp_voting_data_selected <- reactive({
  
  if(is.null(input$cp6map_shape_click)){
    cp_voting_data
  } else {
    cp_voting_data %>% 
      filter(state_name == click_cp6map())
  }
  
})

leafletOutput("cp6map")  

```

### Table {.wide-DT data-width=500}

```{r, community participation voting table }

# Columns to show
cp_voting_cols_selected <- reactive({
             
  if (input$cp_voting_type == "PWD // Voter Turnout (2018)"){
    "(pwd.*turnout_2018|change_in_pwd_voter_turnout)"
  } else if (input$cp_voting_type == "PWOD // Voter Turnout (2018)"){
    "(pwod.*turnout_2018|change_in_pwod_turnout)"
  } else {
    "(pwod.*disability_gap_2018|change_in_disability_gap)"
  }
  
})

# Data table (scroll function for wide data)
DT::renderDataTable({
  
  # Table
  DT::datatable(
    cp_voting_data_selected() %>%
      mutate(across(matches("percent"), percent, scale = 1, accuracy = 0.1),
             across(where(is.numeric), comma)) %>% 
      select(starts_with("state"), matches(cp_voting_cols_selected(), perl = TRUE)),
   options(scrollX = "200px"))
  
})

```














Work/Economic {data-navmenu="National" data-icon="fa-wrench"}
======================================================================

Row {data-height=100}
-----------------------------------------------------------------------

### {.section-divider}

#### Employment

##### Percent of Persons with or without Disabilities

Row {data-height=500}
-----------------------------------------------------------------------

### Map {data-width=500}

```{r, work economic employment map}

# Data for this section
we_employ_data <- work_economic %>% 
  filter(is.na(city)) %>% 
  select("state_name" = state, "state_abbv" = state_abbreviation, 
         total_population:percent_pwod_not_in_the_labor_force,
         population_worked_full_time_year_round:pwod_did_not_work,
         pwd_percentage_of_people_working_from_home:pwod_percentage_of_people_working_from_home) %>% 
  mutate(across(starts_with("percent"), round, 1))

# SF data and palette
we_employ_map_data <- we_employ_data %>% 
    left_join(states_sf, ., by = c("state_name", "state_abbv")) %>% 
    st_transform(4326)
  
# Input for column to map
selectInput("we_employ_type", 
            label = "Select a category", 
            choices = c("PWD // 18-64 // Employed",
                        "PWD // 18-64 // Unemployed",
                        "PWD // 18-64 // Not in Labor Force",
                        "PWD // 18-64 // Work Full Time",
                        "PWD // 18-64 // Work Part Time",
                        "PWD // 16-64 // Work From Home",
                        "PWOD // 18-64 // Employed",
                        "PWOD // 18-64 // Unemployed",
                        "PWOD // 18-64 // Not in Labor Force",
                        "PWOD // 18-64 // Work Full Time",
                        "PWOD // 18-64 // Work Part Time",
                        "PWOD // 16-64 // Work From Home"),
            selected = "PWD // 18-64 // Employed",
            width = "400px")

we_employ_selected <- reactive({
  
  if (input$we_employ_type == "PWD // 18-64 // Employed"){
    "percent_pwd_employed"
  } else if (input$we_employ_type == "PWD // 18-64 // Unemployed"){
    "percent_pwd_unemployed"
  } else if (input$we_employ_type == "PWD // 18-64 // Not in Labor Force"){
    "percent_pwd_not_in_the_labor_force"
  } else if (input$we_employ_type == "PWD // 18-64 // Work Full Time"){
    "pwd_full_time"
  } else if (input$we_employ_type == "PWD // 18-64 // Work Part Time"){
    "pwd_part_time"
  } else if (input$we_employ_type == "PWD // 18-64 // Work From Home"){
    "pwd_percentage_of_people_working_from_home"
  } else if (input$we_employ_type == "PWOD // 18-64 // Employed"){
    "percent_pwod_employed"
  } else if (input$we_employ_type == "PWOD // 18-64 // Unemployed"){
    "percent_pwod_unemployed"
  } else if (input$we_employ_type == "PWOD // 18-64 // Not in Labor Force"){
    "percent_pwod_not_in_the_labor_force"
  } else if (input$we_employ_type == "PWOD // 18-64 // Work Full Time"){
    "pwod_full_time"
  } else if (input$we_employ_type == "PWOD // 18-64 // Work Part Time"){
    "pwod_part_time"
  } else {
    "pwod_percentage_of_people_working_from_home"
  }
  
})

pal_we1 <- reactive ({ 
    
    colorQuantile(palette = input$access_map_palette, 
                  domain = pull(we_employ_data, !!sym(we_employ_selected())),
                  n = 4)
                 
  })
  
# State map
output$we1map <- renderLeaflet({
  
  # Map
  we1map <- we_employ_map_data %>%
    mutate(map_focus = !!sym(we_employ_selected())) %>% 
    leaflet() %>%
    clearShapes() %>%
    addResetMapButton() %>% 
    addPolygons(stroke = TRUE, color = "#444444", weight = 1, smoothFactor = 0, 
                fillColor = ~pal_we1()(map_focus),
                fillOpacity = 1,
                popup = ~paste(state_name, " (", state_abbv, ")", "<br>",
                               percent(map_focus,
                                       scale = 1, accuracy = 0.1)),
                layerId = ~state_name) %>% 
    addLegend(position = "topright", pal = pal_we1(),
              values = ~map_focus,
              labFormat =  function(type, cuts, p) {
                n = length(cuts)
                paste0(as.numeric(cuts)[-n], " &ndash; ", as.numeric(cuts)[-1])
              },
              title = paste0(str_replace_all(input$we_employ_type,
                                             " // ", "<br>"),
                             " (%)"))
  
  we1map
  
})

# Click event for the map
click_we1map <- eventReactive(input$we1map_shape_click, {
  
  x <- input$we1map_shape_click
  y <- x$id
  
  return(y)

})

# Add the clicked state to the map, and remove when a new one is clicked
observe({
  
  req(click_we1map())
  
  we1map <- leafletProxy("we1map") %>%
    removeShape("highlight_state") %>%
    addPolygons(data = we_employ_map_data[we_employ_map_data$state_name == click_we1map(), ], 
                fill = FALSE, weight = 3,
                color = "#00FFFF", opacity = 1, layerId = "highlight_state")
  
})

# Fetch data for the clicked state
we_employ_data_selected <- reactive({
  
  if(is.null(input$we1map_shape_click)){
    we_employ_data
  } else {
    we_employ_data %>% 
      filter(state_name == click_we1map())
  }
  
})

leafletOutput("we1map")  

```

### Table {.wide-DT data-width=500}

```{r, work economic employment table }

# Columns to show
we_employ_cols_selected <- reactive({
             
  if (input$we_employ_type == "PWD // 18-64 // Employed"){
    "pwd.*(?<!un)employed"
  } else if (input$we_employ_type == "PWD // 18-64 // Unemployed"){
    "pwd.*unemployed"
  } else if (input$we_employ_type == "PWD // 18-64 // Not in Labor Force"){
    "pwd.*not_in_the_labor_force"
  } else if (input$we_employ_type == "PWD // 18-64 // Work Full Time"){
    "(population_worked_full_time_year_round_with_a_disability|pwd_full_time)"
  } else if (input$we_employ_type == "PWD // 18-64 // Work Part Time"){
    "(population_worked_less_than_full_time_year_round_with_a_disability|pwod_part_time)"
  } else if (input$we_employ_type == "PWD // 18-64 // Work From Home"){
    "pwd_percentage_of_people_working_from_home"
  } else if (input$we_employ_type == "PWOD // 18-64 // Employed"){
    "pwod.*(?<!un)employed"
  } else if (input$we_employ_type == "PWOD // 18-64 // Unemployed"){
    "pwod.*unemployed"
  } else if (input$we_employ_type == "PWOD // 18-64 // Not in Labor Force"){
    "pwod.*not_in_the_labor_force"
  } else if (input$we_employ_type == "PWOD // 18-64 // Work Full Time"){
    "(population_worked_full_time_year_round_without_a_disability|pwod_full_time)"
  } else if (input$we_employ_type == "PWOD // 18-64 // Work Part Time"){
    "(population_worked_less_than_full_time_year_round_without_a_disability|pwod_part_time)"
  } else {
    "pwod_percentage_of_people_working_from_home"
  }
  
})

# Data table (scroll function for wide data)
DT::renderDataTable({
  
  # Table
  DT::datatable(
    we_employ_data_selected() %>%
      mutate(across(matches("percent"), percent, scale = 1, accuracy = 0.1),
             across(where(is.numeric), comma)) %>% 
      select(starts_with("state"), matches(we_employ_cols_selected(), perl = TRUE)),
   options(scrollX = "200px"))
  
})

```

Row {data-height=100}
-----------------------------------------------------------------------

### {.section-divider}

#### Economic Status

##### Percent of Persons with or without Disabilities

Row {data-height=500}
-----------------------------------------------------------------------

### Map {data-width=500}

```{r, work economic status map}

# Data for this section
we_status_data <- work_economic %>% 
  filter(is.na(city)) %>% 
  select("state_name" = state, "state_abbv" = state_abbreviation,
         pwd_median_individual_income_16_yrs_and_older_with_earnings_in_past_12_months_us_dollars:pwod_median_household_income_include_any_working_age_people_age_21_64_us_dollars,
         pwd_income_in_past_12_months_below_poverty_level:percent_pwod_above_poverty_level,
         percent_of_total_population_receiving_ssi:ssi_as_percent_median_income_percentage,
         number_of_ssi_beneficiaries_18_64:percent_pop_18_64_receiving_ssdi) %>% 
  mutate(across(starts_with("percent"), round, 1))

# SF data and palette
we_status_map_data <- we_status_data %>% 
    left_join(states_sf, ., by = c("state_name", "state_abbv")) %>% 
    st_transform(4326)
  
# Input for column to map
selectInput("we_status_type", 
            label = "Select a category", 
            choices = c("PWD // 16+ // Median Individual Income",
                        "PWD // 21-64 // Median Household Income",
                        "PWD // 18-64 // Below the Poverty Level",
                        "PWOD // 16+ // Median Individual Income",
                        "PWOD // 21-64 // Median Household Income",
                        "PWOD // 18-64 // Below the Poverty Level",
                        "SSI // Percent of Total Population",
                        "SSI // Monthly Payment",
                        "SSI // Percent of Monthly Income",
                        "SSDI // Percent of Total Population"),
            selected = "PWD // 16+ // Median Individual Income",
            width = "400px")

we_status_selected <- reactive({
  
  if (input$we_status_type == "PWD // 16+ // Median Individual Income"){
    "pwd_median_individual_income_16_yrs_and_older_with_earnings_in_past_12_months_us_dollars"
  } else if (input$we_status_type == "PWD // 21-64 // Median Household Income"){
    "pwd_median_household_income_include_any_working_age_people_age_21_64_us_dollars"
  } else if (input$we_status_type == "PWD // 18-64 // Below the Poverty Level"){
    "percent_pwd_below_poverty_level"
  } else if (input$we_status_type == "PWOD // 16+ // Median Individual Income"){
    "pwod_median_individual_income_16_yrs_and_older_with_earnings_in_past_12_months_us_dollars"
  } else if (input$we_status_type == "PWOD // 21-64 // Median Household Income"){
    "pwod_median_household_income_include_any_working_age_people_age_21_64_us_dollars"
  } else if (input$we_status_type == "PWOD // 18-64 // Below the Poverty Level"){
    "percent_pwod_below_poverty_level"
  } else if (input$we_status_type == "SSI // Percent of Total Population"){
    "percent_of_total_population_receiving_ssi"
  } else if (input$we_status_type == "SSI // Monthly Payment"){
    "ssi_monthly_payment_us_dollars"
  } else if (input$we_status_type == "SSI // Percent of Monthly Income"){
    "ssi_as_percent_median_income_percentage"
  } else {
    "percent_pop_18_64_receiving_ssdi"
  }
  
})

pal_we2 <- reactive ({ 
    
    colorQuantile(palette = input$access_map_palette, 
                  domain = pull(we_status_data, !!sym(we_status_selected())),
                  n = 4)
                 
  })
  
# State map
output$we2map <- renderLeaflet({
  
  # Map
  we2map <- we_status_map_data %>%
    mutate(map_focus = !!sym(we_status_selected())) %>% 
    leaflet() %>%
    clearShapes() %>%
    addResetMapButton() %>% 
    addPolygons(stroke = TRUE, color = "#444444", weight = 1, smoothFactor = 0, 
                fillColor = ~pal_we2()(map_focus),
                fillOpacity = 1,
                popup = ~paste(state_name, " (", state_abbv, ")", "<br>",
                               percent(map_focus,
                                       scale = 1, accuracy = 0.1)),
                layerId = ~state_name) %>% 
    addLegend(position = "topright", pal = pal_we2(),
              values = ~map_focus,
              labFormat =  function(type, cuts, p) {
                n = length(cuts)
                paste0(as.numeric(cuts)[-n], " &ndash; ", as.numeric(cuts)[-1])
              },
              title = paste0(str_replace_all(input$we_status_type,
                                             " // ", "<br>"),
                             " (%)"))
  
  we2map
  
})

# Click event for the map
click_we2map <- eventReactive(input$we2map_shape_click, {
  
  x <- input$we2map_shape_click
  y <- x$id
  
  return(y)

})

# Add the clicked state to the map, and remove when a new one is clicked
observe({
  
  req(click_we2map())
  
  we2map <- leafletProxy("we2map") %>%
    removeShape("highlight_state") %>%
    addPolygons(data = we_status_map_data[we_status_map_data$state_name == click_we2map(), ], 
                fill = FALSE, weight = 3,
                color = "#00FFFF", opacity = 1, layerId = "highlight_state")
  
})

# Fetch data for the clicked state
we_status_data_selected <- reactive({
  
  if(is.null(input$we2map_shape_click)){
    we_status_data
  } else {
    we_status_data %>% 
      filter(state_name == click_we2map())
  }
  
})

leafletOutput("we2map")  

```

### Table {.wide-DT data-width=500}

```{r, work economic status table }

# Columns to show
we_status_cols_selected <- reactive({
             
    if (input$we_status_type == "PWD // 16+ // Median Individual Income"){
    "pwd_median_individual_income_16_yrs_and_older_with_earnings_in_past_12_months_us_dollars"
  } else if (input$we_status_type == "PWD // 21-64 // Median Household Income"){
    "pwd_median_household_income_include_any_working_age_people_age_21_64_us_dollars"
  } else if (input$we_status_type == "PWD // 18-64 // Below the Poverty Level"){
    "pwd.*below_poverty_level"
  } else if (input$we_status_type == "PWOD // 16+ // Median Individual Income"){
    "pwod_median_individual_income_16_yrs_and_older_with_earnings_in_past_12_months_us_dollars"
  } else if (input$we_status_type == "PWOD // 21-64 // Median Household Income"){
    "pwod_median_household_income_include_any_working_age_people_age_21_64_us_dollars"
  } else if (input$we_status_type == "PWOD // 18-64 // Below the Poverty Level"){
    "pwod.*below_poverty_level"
  } else if (input$we_status_type %in% c("SSI // Percent of Total Population", "SSI // Monthly Payment", "SSI // Percent of Monthly Income")){
    "ssi"
  } else {
    "ssdi"
  }
  
})

# Data table (scroll function for wide data)
DT::renderDataTable({
  
  # Table
  DT::datatable(
    we_status_data_selected() %>%
      mutate(across(matches("percent"), percent, scale = 1, accuracy = 0.1),
             across(where(is.numeric), comma)) %>% 
      select(starts_with("state"), matches(we_status_cols_selected(), perl = TRUE)),
   options(scrollX = "200px"))
  
})

```

Row {data-height=100}
-----------------------------------------------------------------------

### {.section-divider}

#### Economic Status

##### Percent of Persons with or without Disabilities

Row {data-height=500}
-----------------------------------------------------------------------

### Map {data-width=500}

```{r, work economic affordability map}

# Data for this section
we_afford_data <- work_economic %>% 
  filter(is.na(city)) %>% 
  select("state_name" = state, "state_abbv" = state_abbreviation,
         percent_ssi_for_1_bedroom_percentage, percent_ssi_for_efficiency_apt_percentage,
         x2_bedroom_rental_unit_housing_wage_us_dollars_from_nlihc_org_fy_2019) %>% 
  mutate(across(starts_with("percent"), round, 1))

# SF data and palette
we_afford_map_data <- we_afford_data %>% 
    left_join(states_sf, ., by = c("state_name", "state_abbv")) %>% 
    st_transform(4326)
  
# Input for column to map
selectInput("we_afford_type", 
            label = "Select a category", 
            choices = c("SSI // Percent Needed for Efficiency Apt at FMR",
                        "SSI // Percent Needed for 1-BR Apt at FMR",
                        "Hourly Wage // Needed for 2-BR Apt at FMR"),
            selected = "SSI // Percent Needed for Efficiency Apt at FMR",
            width = "400px")

we_afford_selected <- reactive({
  
  if (input$we_afford_type == "SSI // Percent Needed for Efficiency Apt at FMR"){
    "percent_ssi_for_efficiency_apt_percentage"
  } else if (input$we_afford_type == "SSI // Percent Needed for 1-BR Apt at FMR"){
    "percent_ssi_for_1_bedroom_percentage"
  } else {
    "x2_bedroom_rental_unit_housing_wage_us_dollars_from_nlihc_org_fy_2019"
  }
  
})

pal_we3 <- reactive ({ 
    
    colorQuantile(palette = input$access_map_palette, 
                  domain = pull(we_afford_data, !!sym(we_afford_selected())),
                  n = 4)
                 
  })
  
# State map
output$we3map <- renderLeaflet({
  
  # Map
  we3map <- we_afford_map_data %>%
    mutate(map_focus = !!sym(we_afford_selected())) %>% 
    leaflet() %>%
    clearShapes() %>%
    addResetMapButton() %>% 
    addPolygons(stroke = TRUE, color = "#444444", weight = 1, smoothFactor = 0, 
                fillColor = ~pal_we3()(map_focus),
                fillOpacity = 1,
                popup = ~paste(state_name, " (", state_abbv, ")", "<br>",
                               percent(map_focus,
                                       scale = 1, accuracy = 0.1)),
                layerId = ~state_name) %>% 
    addLegend(position = "topright", pal = pal_we3(),
              values = ~map_focus,
              labFormat =  function(type, cuts, p) {
                n = length(cuts)
                paste0(as.numeric(cuts)[-n], " &ndash; ", as.numeric(cuts)[-1])
              },
              title = paste0(str_replace_all(input$we_afford_type,
                                             " // ", "<br>"),
                             " (%)"))
  
  we3map
  
})

# Click event for the map
click_we3map <- eventReactive(input$we3map_shape_click, {
  
  x <- input$we3map_shape_click
  y <- x$id
  
  return(y)

})

# Add the clicked state to the map, and remove when a new one is clicked
observe({
  
  req(click_we3map())
  
  we3map <- leafletProxy("we3map") %>%
    removeShape("highlight_state") %>%
    addPolygons(data = we_afford_map_data[we_afford_map_data$state_name == click_we3map(), ], 
                fill = FALSE, weight = 3,
                color = "#00FFFF", opacity = 1, layerId = "highlight_state")
  
})

# Fetch data for the clicked state
we_afford_data_selected <- reactive({
  
  if(is.null(input$we3map_shape_click)){
    we_afford_data
  } else {
    we_afford_data %>% 
      filter(state_name == click_we3map())
  }
  
})

leafletOutput("we3map")  

```

### Table {.wide-DT data-width=500}

```{r, work economic affordability table }

# Columns to show
we_afford_cols_selected <- reactive({
             
    if (input$we_afford_type == "SSI // Percent Needed for Efficiency Apt at FMR"){
    "percent_ssi_for_efficiency_apt_percentage"
  } else if (input$we_afford_type == "SSI // Percent Needed for 1-BR Apt at FMR"){
    "percent_ssi_for_1_bedroom_percentage"
  } else {
    "x2_bedroom_rental_unit_housing_wage_us_dollars_from_nlihc_org_fy_2019"
  }
  
})

# Data table (scroll function for wide data)
DT::renderDataTable({
  
  # Table
  DT::datatable(
    we_afford_data_selected() %>%
      mutate(across(matches("percent"), percent, scale = 1, accuracy = 0.1),
             across(where(is.numeric), comma)) %>% 
      select(starts_with("state"), matches(we_afford_cols_selected(), perl = TRUE)),
   options(scrollX = "200px"))
  
})

```








By Metro
======================================================================

Sidebar {.sidebar}
-----------------------------------------------------------------------

```{r metro import}
demo_metro_data <- demographics %>% 
  filter(is.na(city) == FALSE) %>% 
  select("state_name" = state, "state_abbv" = abbrev, city,
         pwd, total_population, contains("percent")) %>%  # This is cleaner than listing out every variable
  mutate_if(is.numeric, round, 1)
```

```{r}

# # Set up data download
# data_for_dl <- reactive({
#   
#   dat <- select(metro()@data, GEOID, state, county, white, black, hispanic, asian, total, 
#                 entropy, distmeters = distance, distmiles)
#   
# })

rm_opt <- list('plugins' = list('remove_button'), # Adds removal "x" to selectize inputs
               'create' = TRUE,
               'persist' = FALSE)

metro_name <- data.frame(city = demo_metro_data$city, state = demo_metro_data$state_abbv, full = paste0(demo_metro_data$city, ", ", demo_metro_data$state_abbv))
demographic_var <- data.frame(option = names(demo_metro_data %>% select(pwd:percent_pwd_female))) # Probably not efficient, and would need to be changed if the table-column order changed, but it'll work for now.

# selectInput('metro_name', label = "Select a metropolitan area", choices = metro_name$full, selected = metro_name[[1]])
select
selectizeInput('metro_select', 'Select Metro Areas to Compare', choices = metro_name[,3], multiple = TRUE, options = rm_opt)
selectizeInput('var_select', label = "Select a demographic variable", choices = demographic_var, multiple = TRUE, options = rm_opt)

metro_select <- reactive({ 
  if(is.null(input$metro_select)){ ### I think that this logic works, and requires less input from the user
    metro_name$full
  }else{
      input$metro_select
    }
})

var_select <- reactive ({
  if(is.null(input$var_select)){
      demographic_var$option
    }else{
      input$var_select
    }
})

```
<br>

Some type of checkbox/dropdown input that allows the map/chart to be dependent on selected metro

Sidebars are great places to include download links (csv, shp, etc) for users to access

Row
-----------------------------------------------------------------------

<!-- ### Map -->
<!-- ```{r } -->
<!-- ### leaflet map of census tracts w/in metro area, thematic map of selected variable -->
<!-- # Though the current data is at the metro level, so this wouldn't be easily implemented. -->
<!-- #  -->
<!-- ``` -->

### Chart

```{r }

DT::renderDataTable({
  
  if(is.null(metro_select()) & is.null(var_select())){
    DT::datatable(
      demo_metro_data %>% 
        mutate(full = paste0(city, ", ", state_abbv)) %>%
        select(full, demographic_var$option) %>%
        rename("City" = full),
      options(scrollX = "200px")
      )
  }else{
     DT::datatable(
      demo_metro_data %>% 
        mutate(full = paste0(city, ", ", state_abbv)) %>%
        select(full, var_select()) %>%
        rename("City" = full) %>%
        filter(City %in% metro_select()),
      options(scrollX = "200px")
      )
  }

})

```

Row
-----------------------------------------------------------------------

### Interactive Viz

```{r }

output$metro_plot <- renderPlot({

    demo_metro_data %>%
      mutate(full = paste0(city, ", ", state_abbv)) %>%
      select(full, var_select()) %>%
      rename("City" = full) %>%
      filter(City %in% metro_select(), City != "United States, USA") %>%
      ggplot(aes(x = reorder(City, !!sym(var_select()[1])), y = !!sym(var_select()[1]))) + ### I think there's a way to abstract this instead of calling the first column after full, but I'll do it later
      geom_col() + 
      labs(y = var_select()[1], x = "City") +
      coord_flip()

})


plotOutput("metro_plot")

```



Data {data-navmenu="Download" data-icon="fa-database"}
======================================================================

Sidebar {.sidebar}
-----------------------------------------------------------------------

<br>

```{r, data download sidebar}

# ====================
# Filters
# ====================

# Define inputs
radioButtons(inputId = "data_download_national",
             label = "Select an Area of Interest",
             choices = c("Demographics", "Community Living", 
                             "Community Participation", "Work/Economic"),
             selected = "Demographics")

# Restrict statistic breakdown based on type
data_download_national_selected <- reactive({
  
  if (input$data_download_national == "Demographics"){
    demographics
  } else if (input$data_download_national == "Community Living"){
    community_living
  } else if (input$data_download_national == "Community Participation"){
    community_participation
  } else {
    work_economic
  }
  
})

```

Row {data-height=800}
-----------------------------------------------------------------------

### Selected Data for Download {.download-DT}

```{r, data download table}

# Selected data for download
output$data_download_table <- DT::renderDataTable({
  
  DT::datatable(data_download_national_selected(),
                fillContainer = TRUE,
                extensions = "Buttons",
                options = list(dom = "Bfrtip",
                               buttons = c("copy", "csv", "excel", "pdf", "print"),
                               bPaginate = FALSE,
                               scrollX = "200px",
                               scrollY = "800px",
                               pageLength = dim(data_download_national_selected())[1]))
  
})

DT::dataTableOutput("data_download_table", width = 50)

```



Fact Sheets {data-navmenu="Download" data-icon="fa-file-alt"}
======================================================================

Sidebar {.sidebar}
-----------------------------------------------------------------------

```{r, fact sheet download sidebar}

# ====================
# Lookups for filters
# ====================

# Demographics
demographics_lu <- names(demographics) %>% 
  as_tibble_col(column_name = "column_name") %>% 
  mutate(column_type =
           case_when(str_detect(string = column_name,
                                pattern = "percent") ~
                       "percent",
                     TRUE ~ "value"),
         filter_temp = 
           case_when(column_name %in%
                       c("pwd",
                         "percent_of_total_population_with_a_disability") ~
                       "general __ General",
                     column_name %in%
                       c("pwd_18_64_years",
                         "pwd_65_years") ~
                       "age __ Age",
                     TRUE ~ NA_character_)) %>% 
  filter(!is.na(filter_temp)) %>% 
  separate(col = "filter_temp", 
           into = c("filter_value", "filter_label"),
           sep = " __ ")

# Community Living
community_living_lu <- names(community_living) %>% 
  as_tibble_col(column_name = "column_name") %>% 
  mutate(column_type =
           case_when(str_detect(string = column_name,
                                pattern = "percent") ~
                       "percent",
                     TRUE ~ "value"),
         filter_temp = 
           case_when(column_name %in%
                       c("pwd_in_institutionalized_group_quarters",
                         "percent_pwd_institution") ~
                       "institution_pop __ PWD Living in Institutional Residence",
                     column_name %in%
                       c("pwd_in_home",
                         "percent_pwd_home") ~
                       "home_pop __ PWD Living in Home Residence",
                     column_name %in%
                       c("pwd_in_non_institutional_group_quarters",
                         "percent_pwd_other_group_quarters") ~
                       "othergq_pop __ PWD Living in Other Group Quarters Residence",
                     column_name %in%
                       c("total_population_in_nursing_18_64",
                         "percent_of_pwd_18_64_in_nursing") ~
                       "nursing_working_pop __ PWD of Working Age, Living in Nursing Home",
                     TRUE ~ NA_character_)) %>% 
  filter(!is.na(filter_temp)) %>% 
  separate(col = "filter_temp", 
           into = c("filter_value", "filter_label"),
           sep = " __ ")

# ====================
# Filters
# ====================

# Define inputs
radioButtons(inputId = "fact_sheet_national",
             label = "Select an Area of Interest",
             choices = c("Demographics", "Community Living", 
                             "Community Participation", "Work/Economic"))

# Restrict statistic breakdown based on type
fact_sheet_national_selected <- reactive({
  
  if (input$fact_sheet_national == "Demographics"){
    demographics_lu
  } else if (input$fact_sheet_national == "Community Living"){
    community_living_lu
  # } else if (input$fact_sheet_national == "Community Living"){
  #   community_participation_lu
  } else {
    NA
  }
  
})

# Statistics dropdown to given area
renderUI({ 
  
  selectInput(inputId = "fact_sheet_stat", 
              label = "Select a Statistic", 
              choices = unique(fact_sheet_national_selected()$filter_label))
  
})

# Restrict statistic breakdown based on type
stat_base <- reactive({
  
  if (input$fact_sheet_national == "Demographics"){
    demographics
  } else if (input$fact_sheet_national == "Community Living"){
    community_living
  # } else if (input$fact_sheet_national == "Community Participation"){
  #   community_participation
  } else {
    NA
  }
  
})

# Select columns based on input
stat_subset <- reactive({
  
  stat_base() %>% 
    select(state:abbrev,
           all_of(fact_sheet_national_selected() %>% 
                    filter(filter_label == input$fact_sheet_stat) %>% 
                    pull(column_names)))
    
})


```



Accessibility
======================================================================

Row
-----------------------------------------------------------------------

###  {.long-row}

```{r}

# Map palette
selectInput(inputId = "access_map_palette",
            label = h5("Select a color palette for maps:"),
            choices = list("Yellow-Orange-Brown" = "YlOrBr", 
                           "Yellow-Orange-Red" = "YlOrRd", 
                           "Green-Blue" = "GnBu"),
            selected = "Yellow-Orange-Brown")


# GGplot themes and colors
access_ggplot_themes <- list(
  "The Economist" = list(theme_economist(), scale_fill_economist(), scale_color_economist()),
  "Five Thirty Eight" = list(theme_fivethirtyeight(), scale_fill_economist(), scale_color_fivethirtyeight()),
  "Highcharts" = list(theme_hc(), scale_fill_hc(), scale_color_hc()),
  "Ipsum" = list(theme_ipsum(), scale_fill_colorblind(), scale_color_colorblind()),
  "Light" = list(theme_light(), scale_fill_colorblind(), scale_color_colorblind()),
  "Minimal" = list(theme_minimal(),scale_fill_ordinal(), scale_color_ordinal()),
  "Stata" = list(theme_stata(), scale_fill_stata(), scale_color_stata()))

selectInput(inputId = "access_ggplot_theme", 
            label = h5("Select a theme for plots:"), 
            choices = names(access_ggplot_themes),
            selected = "Ipsum")

ggplot_theme_selected <- reactive({ access_ggplot_themes[[input$access_ggplot_theme]][1] })
ggplot_fill_selected <- reactive({ access_ggplot_themes[[input$access_ggplot_theme]][2] }) 
ggplot_color_selected <- reactive({ access_ggplot_themes[[input$access_ggplot_theme]][3] }) 

```



<!-- CSS for dashboard  -->
<style  type="text/css">

/* #################### */
/* Fonts */
/* #################### */

/* Headers */
h2,h3,h4,h5 { 
  font-weight: bold;
}

/* #################### */
/* Coloring */
/* #################### */

/* Leaflet border */
.leaflet .legend i{
    border-left:1px solid #000000;
    border-right:1px solid #000000;
    border-top:1px solid #000000;
    border-bottom:1px solid #000000;
}

/* Leaflet background */
.leaflet-container {
  background: #696969;
}

/* Section dividers */
.section-divider { 
  background-color: #CCCCCC;
  color: #000000;
}

/* Colors for map palette dropdown */
#access_map_palette ~ .selectize-control .option[data-value=YlOrBr]{ 
  background-image: linear-gradient(to right, white, #ffffd4, #fed98e, #fe9929, #cc4c02) !important;
  background-size: auto !important;
}

#access_map_palette ~ .selectize-control .option[data-value=YlOrRd]{ 
  background-image: linear-gradient(to right, white , #ffffb2, #fecc5c, #fd8d3c, #e31a1c) !important;
  background-size: auto !important;
}

#access_map_palette ~ .selectize-control .option[data-value=GnBu]{ 
  background-image: linear-gradient(to right, white , #f0f9e8, #bae4bc, #7bccc4, #2b8cbe) !important;
  background-size: auto !important;
}



/* #################### */
/* Containers */
/* #################### */

/* Set max length for dropdowns */
.selectize-dropdown-content {
padding: 10px;
}

/* Allow dropdowns to be visible for short containers */
#access_ggplot_theme+ div>.selectize-dropdown, #access_map_palette+ div>.selectize-dropdown {
  position: static;
}

/* Have dropdowns display on top of Leaflet */
.selectize-dropdown {
  z-index: 10000;
  overflow-y: auto;
}

/* Scroll overflow for DT */
.wide-DT {
  overflow-x: scroll;
}

/* Scroll overflow for Download */
.download-DT {
  overflow-x: scroll;
  overflow-y: scroll;
}

</style>
