---
title: "ADA-PARC Census Database Builder Tool"
output:
  html_document:
    toc: TRUE
    toc_float: TRUE
    code_folding: hide
editor_options: 
  chunk_output_type: console
runtime: shiny
---

```{r setup, include=FALSE}

# Libraries
library(tidyverse);library(readxl)
library(tigris);library(sf);library(janitor)
library(tidycensus);library(viridis);library(tmap)
library(RPostgres);library(RPostgreSQL);library(DBI)
library(geojsonsf);library(mongolite)
library(shiny); library(shinyWidgets)

# Set working document, options
setwd(here::here())
options(scipen = 999, dplyr.summarise.inform = FALSE, tigris_use_cache = TRUE)
knitr::opts_chunk$set(echo = FALSE)

# Load API keys and database connection information
source("secret.R", local = TRUE)

```

### Background

This interactive walkthrough tool allows users to upload specific American Community Survey (ACS) data related to people with disabilities to the MongoDB database powering the [ADA-PARC Data Dashboard](https://ada-parc.shinyapps.io/ada_parc/). The rest of the document is organized by the various geographies used in the ADA-PARC dashboard: States, Cities (or Places), and Tracts.

### States

#### Select ACS Components

Use the following inputs to download ACS data at the state level. 

```{r states-input}

# Dataset
selectInput(inputId = "states_acs_dataset",
            label = "Select a dataset:",
            choices = list(`5-Year ACS` = list("Default (Detailed)" = "acs5",
                                               "Subject" = "acs5/subject", 
                                               "Profile" = "acs5/profile"),
                           `3-Year ACS` = list("Default (Detailed)" = "acs3",
                                               "Subject" = "acs3/subject", 
                                               "Profile" = "acs3/profile"),
                           `1-Year ACS` = list("Default (Detailed)" = "acs1",
                                               "Subject" = "acs1/subject", 
                                               "Profile" = "acs1/profile"),
                           `Summary File` = list("3-Year" = "sf3", 
                                                 "1-Year" = "sf1")),
            selected = "acs5/subject")

# Year
selectInput(inputId = "states_acs_year",
            label = "Select a data endpoint year:",
            choices = c(2005:2019),
            selected = 2019)

# State variables for selection
states_acs_vars_ref <- reactive({
  
  load_variables(year = input$states_acs_year,
                 dataset =  input$states_acs_dataset, 
                 cache = TRUE) %>% 
    filter(!is.na(concept)) %>% 
    mutate(table_name = gsub( "_.*$", "", name),
           label = gsub("!!", "; ", label),
           shiny_input_label = paste0(table_name, ": ", str_to_title(concept)))
  
})

# Static check
states_acs_vars_ref <- load_variables(year = 2019,
                                      dataset = "acs5/subject", 
                                      cache = TRUE) %>% 
  filter(!is.na(concept)) %>% 
  mutate(table_name = gsub( "_.*$", "", name),
         label = gsub("!!", "; ", label),
         shiny_input_label = paste0(table_name, ": ", str_to_title(concept)))

# # Tables
# test <- states_acs_vars_ref %>% 
#   tabyl(shiny_input_label)
# 
# 
# states_acs_vars_selected <- states_acs_vars_ref %>% 
#   filter(str_detect(name, pattern = "(^S181(0|1)_*)|(^S26(01A|02)_*)")) %>% 
#   filter(!str_detect(label, pattern = "DISABILITY TYPE BY DETAILED AGE")) %>% # Removes detailed age data
#   mutate(table_name = gsub( "_.*$", "", name),
#          label = gsub("!!", "; ", label))

```

### Cities

#### Select ACS Components

You can also embed plots, for example:

#### Select Cities (Census-Defined Places) 

```{r cities-location-input}

most_populated <- get_estimates(geography = "place",
                                year = 2018,
                                product = "population",
                                geometry = FALSE,
                                output = "wide") %>% 
  arrange(desc(POP)) %>% 
  head(200)

```
